---
# IMPORTANT: Change settings here, but DO NOT change the spacing.
# Remove comments and add values where applicable.
# The descriptions below should be self-explanatory

title: "Literature Review"
#subtitle: "This will appear as Right Header"

documentclass: "elsarticle"

# --------- Thesis title (Optional - set to FALSE by default).
# You can move the details below around as you please.
Thesis_FP: FALSE
# Entry1: "An unbelievable study with a title spanning multiple lines."
# Entry2: "\\textbf{Some Guy}" # textbf for bold
# Entry3: "A thesis submitted toward the degree of Doctor of Philosophy"
# Uni_Logo: Tex/Logo.png # Place a logo in the indicated location (from your root, e.g. defaults to ~/Tex/Logo.png) and uncomment this line. Leave uncommented for no image
# Logo_width: 0.3 # If using a logo - use this to set width (size) of image
# Entry4: "Under the supervision of: \\vfill Prof. Joe Smith and Dr. Frank Smith"
# Entry5: "Stellenbosch University"
# Entry6: April 2020
# Entry7:
# Entry8:

# --------- Front Page
# Comment: ----- Follow this pattern for up to 5 authors
AddTitle: TRUE # Use FALSE when submitting to peer reviewed platform. This will remove author names.
Author1: "Gabriel Rambanapasi"  # First Author - note the thanks message displayed as an italic footnote of first page.
Ref1: "Stellenbosch University, Cape Town, South Africa" # First Author's Affiliation
Email1: "gabriel.rams44\\@gmail.com" # First Author's Email address

# Author2: "John Smith"
# Ref2: "Some other Institution, Cape Town, South Africa"
# Email2: "John\\@gmail.com"
# CommonAffiliation_12: TRUE # If Author 1 and 2 have a common affiliation. Works with _13, _23, etc.

# Author3: "John Doe"
# Email3: "Joe\\@gmail.com"

CorrespAuthor_1: TRUE  # If corresponding author is author 3, e.g., use CorrespAuthor_3: TRUE

# Comment out below to remove both. JEL Codes only given if keywords also given.
keywords: "" # Use \\sep to separate
JELCodes: ""

# ----- Manage headers and footers:
#BottomLFooter: $Title$
#BottomCFooter:
#TopLHeader: \leftmark # Adds section name at topleft. Remove comment to add it.
BottomRFooter: "\\footnotesize Page \\thepage" # Add a '#' before this line to remove footer.
addtoprule: TRUE
addfootrule: TRUE               # Use if footers added. Add '#' to remove line.

# --------- page margins:
margin: 2.3 # Sides
bottom: 2 # bottom
top: 2.5 # Top
HardSet_layout: TRUE # Hard-set the spacing of words in your document. This will stop LaTeX squashing text to fit on pages, e.g.
# This is done by hard-setting the spacing dimensions. Set to FALSE if you want LaTeX to optimize this for your paper.

# --------- Line numbers
linenumbers: FALSE # Used when submitting to journal

# ---------- References settings:
# You can download cls format here: https://www.zotero.org/ - simply search for your institution. You can also edit and save cls formats here: https://editor.citationstyles.org/about/
# Hit download, store it in Tex/ folder, and change reference below - easy.
bibliography: Tex/ref.bib       # Do not edit: Keep this naming convention and location.
csl: Tex/harvard-stellenbosch-university.csl # referencing format used.
# By default, the bibliography only displays the cited references. If you want to change this, you can comment out one of the following:
nocite: '@*' # Add all items in bibliography, whether cited or not
 # nocite: |  # add specific references that aren't cited
# @grinold2000
#  @Someoneelse2010

# ---------- General:
RemovePreprintSubmittedTo: TRUE  # Removes the 'preprint submitted to...' at bottom of titlepage
Journal: "Journal of Finance"   # Journal that the paper will be submitting to, if RemovePreprintSubmittedTo is set to TRUE.
toc: FALSE                       # Add a table of contents
numbersections: TRUE             # Should sections (and thus figures and tables) be numbered?
fontsize: 11pt                  # Set fontsize
linestretch: 1.5                # Set distance between lines.
link-citations: TRUE            # This creates dynamic links to the papers in reference list.

### Adding additional latex packages:
# header-includes:
#    - \usepackage{colortbl} # Add additional packages here.

output:
  pdf_document:
    keep_tex: TRUE
    template: Tex/TexDefault.txt
    fig_width: 3.5 # Adjust default figure sizes. This can also be done in the chunks of the text.
    fig_height: 3.5
abstract: |

---

<!-- First: Set your default preferences for chunk options: -->

<!-- If you want a chunk's code to be printed, set echo = TRUE. message = FALSE stops R printing ugly package loading details in your final paper too. I also suggest setting warning = FALSE and checking for warnings in R, else you might find ugly warnings in your paper. -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')
# Note: Include = FALSE implies the code is executed, but not printed in your pdf.
# warning and message = FALSE implies ugly messages and warnings are removed from your pdf.
# These should be picked up when you execute the command chunks (code sections below) in your rmd, not printed in your paper!

# Lets load in example data, and see how this can be stored and later called from your 'data' folder.
if(!require("tidyverse")) install.packages("tidyverse")
library(gt)
library(tidyverse)
library(huxtable)
library(kableExtra)
list.literature <- readxl::read_xlsx("data/Literature Summary Table.xlsx")

# Notice that as you are working in a .Rproj file (I am assuming you are) - the relative paths of your directories start at your specified root.
# This means that when working in a .Rproj file, you never need to use getwd() - it is assumed as your base root automatically.


```


<!-- ############################## -->
<!-- # Start Writing here: -->
<!-- ############################## -->

# Literature Review \label{Literature Review}

Dividends are cash payouts that companies use to distribute capital to their shareholders. They can take various forms, such as cash, stock, liquidating, scrip, or property [baker2009understanding]. However, cash dividends are the most common type. The decision to issue dividends is typically made by the board of directors, taking into account the company's operating needs for a given financial year. When a dividend is announced, it has an impact on the financial statements of a company. Resultantly, dividend announcements create a liability which impacts the balance sheet by increasing the current liabilities and decreases shareholder equity, specifically retained earnings, on the balance @baker2009understanding[p.374]. In other words, the company incurs an obligation to pay out the dividend, and the value of the company retained by shareholders decreases accordingly. Various literature have shown that in some countries shareholder values decreases in line with dividend payments. @vijayakumar2010effect, @hussainey2011dividend and @masum2014dividend show negative effect on prices on ex dividend day following the payments of dividends. This effectively means that value of a shareholder remains the same as capital its just swapped for cash. 

Cash dividends, although widely used, are not as tax-efficient as other types of capital distributions, such as share buybacks or stock repurchases. In this form of capital redistribution, a firm exchanges assets for outstanding shares, which shrinks the company’s assets by the amount of cash paid out. This action too reduces both its borrowing base and the shareholders’ aggregate equity @baker2009understanding[p.429]. A clear benefit to the company is that it is more flexible when compared to the rigid dividend payout structures. To most higher net worth investors, tax benefits in the form of lower capital gains taxes result in greater preference for sharebuybacks.  It is thus no surprise that this form of earnings redistribution has gained traction in some advanced economies such as the US (with the Financial Times recently reporting that announced stock buybacks in the US reached an all time high of $437 billion in 2018).  Surprisingly, their adoption has been relatively slow in some emerging economies. According to a study by @wesson2014market, there were only 195 open market share repurchases announced in South Africa from 1999 to 2009. In comparison, @manconi2014buybacks estimated that share repurchases constituted approximately 58% of total announcements in the United States, 15% in Canada, and 11% in Japan over the same period, indicative of a significant disparity in the adoption of share buybacks across the world, despite their popularity in the United States.  

The logical question then is why do firms pay dividends? @miller1985dividend opines that dividends are irrelevant (MM theory), he argues that shareholders are indifferent to dividend payments, implying that there is no optimal dividend policy. Following this school of thought implies that all dividend policies are equally good and thus payments of dividends could easily be reinvested in shares and make no difference to share holder wealth. However, the MM theorem fails to consider real-world market imperfections that may give relevance to dividend payments. Considering these constraints the dividend puzzle gives an interesting take on its relevance and irrelevance, suggesting that dividends reduce equity value and make investors worse off @black1996dividend. However, dividends can be seen as a reward to investors who bear the risk associated with their investments. Also, dividends can be considered a return on investment rather than relying solely on capital gains @black1996dividend. Various literature has emerged trying to solve the puzzel, either supporting irrelevance or relevance in dividend payments.

Global assets market face multiple constraints or imperfections namely transaction costs (e.g., taxes and flotation costs), information asymmetry, and principal-agent problems @baker2009understanding. Taxes play a role in the argument for dividend relevance. Different investors may be attracted to different stocks based on their tax treatments, thus investors choose stocks based on their individual investment needs @van2013advanced @baker2009understanding. However, supporters of the MM theorem argue that changes in dividend policy should not significantly impact stock prices due to the substitution effect. According to this effect, allocation decisions of firms occur almost simultaneously, resulting in a net zero effect on prices [baker2009understanding]. Flotation costs refer to the opportunity costs incurred by a firm when paying dividends. By distributing dividends, companies forego opportunities to expand their operations using retained earnings. In a world without flotation costs, as suggested by the MM theorem, management would be indifferent between issuing dividends and borrowing from the market. However, in reality, external financing comes at a higher cost, leading to trade-offs in dividend policy decisions. 

Information asymmetry between shareholders and managers is another factor that gives relevance to dividend payments. Managers of businesses typically have greater knowledge of operations thus value of a business at any given point more than shareholders. As such,  investors rely on dividend announcements to assess a company's valuation. Dividend signaling conveys information about the company's quality @al2018revisiting  and @baker1999corporate. Investors compare dividend announcements to historical levels while considering company fundamentals. However, there is a risk of manipulation by management, making the dividend signal imperfect for determining share prices. Extending the argument on information asymmetry leads to the principal-agent problem, where management and shareholders may have differing goals for the use of retained earnings, leading to conflict [baker2009understanding]. The free cash flow hypothesis suggests that dividend payments force management to raise capital from external sources, which increases borrowing costs and scrutiny from capital markets. This, in turn, reduces management's ability to make sub optimal investments [baker2009understanding].

Dividend payments and growth in dividends provides a return cue and over the years studies on dividend signaling can be categorized into academic return signaling studies and practitioner-oriented long-term return studies. Academic studies, such as @fama1988permanent, found a positive correlation between increasing predictive power and longer forecast horizons. However, subsequent studies like @ang2007stock found no evidence of long-term predictability in stock returns when considering finite sample influence. This suggests that dividend yield may not be a reliable predictor of subsequent returns. One possible reason for this declining predictive power is the increasing use of share buybacks as an alternative means for capital distribution, which reduces the contribution of dividend yield to total return [robertson2006dividends].

On the other hand, practitioner-oriented literature focuses on the long-term returns of systematic dividend portfolios. One popular strategy is the "Dogs of the Dow (DOD)," which involves constructing a portfolio of the top 10 highest-paying dividend stocks on the Dow Jones Industrial Index at the beginning of the year based on the dividends paid in the previous 12 months, therefore this entail deploying a high yield strategy. The most common methodology used in The portfolio is held for 12 months, and the process is repeated annually. Various studies have examined the DOD strategy or similar high-yield dividend strategies in different time periods and regions, consistently showing superior risk-adjusted returns compared to the market index. Examples of such studies include @lemmon2015dividend in Hong Kong, @brzeszczynski2007dividend in Poland, @visscher2003dividend in Canada, @filbeck1997 in Britian, and @wang2011dogs in China. More recently, @filbeck2017dividend investigated the performance of DOD against a high-yield portfolio of Fortune Most Desired Companies (MAC) compared to the Dow Jones Industrial Average and the S&P 500. The study found significantly higher risk-adjusted returns for the DOD strategy.

\newpage
```{r}

Table <- list.literature %>% 
  gt() %>%
  tab_header(
    title = "Global Dividend Portfolio Signalling Results"
  ) %>% 
  tab_options(
    table.font.size = 10 )
Table
```

\newpage
# Methodology 

## Tax considerations

Portfolio theory was developed in a perfect world without friction. In practice, frictions need to be considered and in portfolio construction this often entails considering the effect of taxes on income and capital gains as they can erode returns and significantly alter risks and return characteristics of shares. The contribution of dividends and capital gains to total return can lead to varying tax efficiencies for shares as most  jurisdictions imposed higher taxes than on capital gains. Therefore shares with higher contribution of dividends will be less tax efficient than those with a higher capital gains component and with timing most jurisdictions tax dividends in the year that they are received^{See Deloitte’s tax guides and country highlights: https://dits.deloitte.com/#TaxGuides}.

Jurisdictional laws can also affect the distribution of taxable returns amongst shares depending on their class namely ordinary shares or preferred shares. Preferred shares are viewed as a substitute for bonds and income from preferred shares are often given tax at a lower rate than those from dividends from ordinary shares.

We will not survey global tax regimes or incorporate all potential tax complexities into the portfolio construction but  assume a  high level commonalities exists amongst all jurisdictions this study  uses. This is a resonable assumption considering  the summary of taxes on dividends and capital gains from major economies.  For simplicity, we will assume a basic tax regime  includes the key elements of investment-related taxes that are representative of what a typical taxable asset owner of a global portfolio will contend with. The proposed methodology to employ on the dividend portfolios use the following methodology. 

$$
r_{a t}=p_d r_{p t}\left(1-t_d\right)+p_a r_{p t}\left(1-t_{c g}\right)
$$
where
$r_{a t}$ the after tax return, 
$p_d=$ the proportion of $r_{p t}$ attributed to dividend income, 
$p_a=$ the proportion of $r_{p t}$ attributed to price appreciation, 
$t_d=$ the dividend tax rate and 
$t_{c g}=$ the capital gains tax rate

\newpage
## Portfolio Construction 

First, we rebalance at the end of March and September and construct fully invested, long only portfolios. On each re balancing date, we first take the top 100 stocks by market
capitalization (MC), and then select the top quintile (20 stocks) based on the relevant signal scores . We then apply 25bps trading costs to both buying and selling of stocks, and (where applicable) replace delisted stocks with cash.

We will then use total return values, adjust for stock splits and other distorting effects on prices to calculate portfolio returns. We also carefully apply back-dated adjustments to dividends paid to accurately arrive at on-the-day dividends and actual closing prices when calculating our Dividend Yield and Dividend Per Share Growth measures.

We also apply at each rebalancing several portfolio optimization routines (minimum variance, equal risk contribution (ERC), mean-variance and max diversification measures. The optimizations are constrained to have minimum and maximum weight exposure of 0.5 and 1.5 times the equal weighted alternative.With our quintile portfolios, this implies weights ranging between 2.5% and 7.5%.

Following this we will construct back-tests on the subset of local data for the choose dividend signal portfolios. The factor portfolios considered are as follows 

\newpage
# References {-}

<div id="refs"></div>



