\documentclass[11pt,preprint, authoryear]{elsarticle}

\usepackage{lmodern}
%%%% My spacing
\usepackage{setspace}
\setstretch{2}
\DeclareMathSizes{12}{14}{10}{10}

% Wrap around which gives all figures included the [H] command, or places it "here". This can be tedious to code in Rmarkdown.
\usepackage{float}
\let\origfigure\figure
\let\endorigfigure\endfigure
\renewenvironment{figure}[1][2] {
    \expandafter\origfigure\expandafter[H]
} {
    \endorigfigure
}

\let\origtable\table
\let\endorigtable\endtable
\renewenvironment{table}[1][2] {
    \expandafter\origtable\expandafter[H]
} {
    \endorigtable
}


\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi

\usepackage{amssymb, amsmath, amsthm, amsfonts}

\def\bibsection{\section*{References}} %%% Make "References" appear before bibliography


\usepackage[round]{natbib}

\usepackage{longtable}
\usepackage[margin=2.3cm,bottom=2cm,top=2.5cm, includefoot]{geometry}
\usepackage{fancyhdr}
\usepackage[bottom, hang, flushmargin]{footmisc}
\usepackage{graphicx}
\numberwithin{equation}{section}
\numberwithin{figure}{section}
\numberwithin{table}{section}
\setlength{\parindent}{0cm}
\setlength{\parskip}{1.3ex plus 0.5ex minus 0.3ex}
\usepackage{textcomp}
\renewcommand{\headrulewidth}{0.2pt}
\renewcommand{\footrulewidth}{0.3pt}

\usepackage{array}
\newcolumntype{x}[1]{>{\centering\arraybackslash\hspace{0pt}}p{#1}}

%%%%  Remove the "preprint submitted to" part. Don't worry about this either, it just looks better without it:
\makeatletter
\def\ps@pprintTitle{%
  \let\@oddhead\@empty
  \let\@evenhead\@empty
  \let\@oddfoot\@empty
  \let\@evenfoot\@oddfoot
}
\makeatother

 \def\tightlist{} % This allows for subbullets!

\usepackage{hyperref}
\hypersetup{breaklinks=true,
            bookmarks=true,
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=blue,
            pdfborder={0 0 0}}


% The following packages allow huxtable to work:
\usepackage{siunitx}
\usepackage{multirow}
\usepackage{hhline}
\usepackage{calc}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{caption}


\newenvironment{columns}[1][]{}{}

\newenvironment{column}[1]{\begin{minipage}{#1}\ignorespaces}{%
\end{minipage}
\ifhmode\unskip\fi
\aftergroup\useignorespacesandallpars}

\def\useignorespacesandallpars#1\ignorespaces\fi{%
#1\fi\ignorespacesandallpars}

\makeatletter
\def\ignorespacesandallpars{%
  \@ifnextchar\par
    {\expandafter\ignorespacesandallpars\@gobble}%
    {}%
}
\makeatother

\newenvironment{CSLReferences}[2]{%
}

\urlstyle{same}  % don't use monospace font for urls
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{5}

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}

%%% Include extra packages specified by user
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{caption}

%%% Hard setting column skips for reports - this ensures greater consistency and control over the length settings in the document.
%% page layout
%% paragraphs
\setlength{\baselineskip}{12pt plus 0pt minus 0pt}
\setlength{\parskip}{12pt plus 0pt minus 0pt}
\setlength{\parindent}{0pt plus 0pt minus 0pt}
%% floats
\setlength{\floatsep}{12pt plus 0 pt minus 0pt}
\setlength{\textfloatsep}{20pt plus 0pt minus 0pt}
\setlength{\intextsep}{14pt plus 0pt minus 0pt}
\setlength{\dbltextfloatsep}{20pt plus 0pt minus 0pt}
\setlength{\dblfloatsep}{14pt plus 0pt minus 0pt}
%% maths
\setlength{\abovedisplayskip}{12pt plus 0pt minus 0pt}
\setlength{\belowdisplayskip}{12pt plus 0pt minus 0pt}
%% lists
\setlength{\topsep}{10pt plus 0pt minus 0pt}
\setlength{\partopsep}{3pt plus 0pt minus 0pt}
\setlength{\itemsep}{5pt plus 0pt minus 0pt}
\setlength{\labelsep}{8mm plus 0mm minus 0mm}
\setlength{\parsep}{\the\parskip}
\setlength{\listparindent}{\the\parindent}
%% verbatim
\setlength{\fboxsep}{5pt plus 0pt minus 0pt}



\begin{document}



\begin{frontmatter}  %

\title{Literature Review}

% Set to FALSE if wanting to remove title (for submission)




\author[Add1]{Gabriel Rambanapasi}
\ead{gabriel.rams44@gmail.com}





\address[Add1]{Stellenbosch University, Cape Town, South Africa}

\cortext[cor]{Corresponding author: Gabriel Rambanapasi}


\vspace{1cm}





\vspace{0.5cm}

\end{frontmatter}

\setcounter{footnote}{0}



%________________________
% Header and Footers
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\pagestyle{fancy}
\chead{}
\rhead{}
\lfoot{}
\rfoot{\footnotesize Page \thepage}
\lhead{}
%\rfoot{\footnotesize Page \thepage } % "e.g. Page 2"
\cfoot{}

%\setlength\headheight{30pt}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%________________________

\headsep 35pt % So that header does not go over title




\hypertarget{literature-review}{%
\section{\texorpdfstring{Literature Review
\label{Literature Review}}{Literature Review }}\label{literature-review}}

Dividends are cash payouts that companies use to distribute capital to
their shareholders. They can take various forms, such as cash, stock,
liquidating, scrip, or property Baker \& Powell
(\protect\hyperlink{ref-baker2009understanding}{2009}). However, cash
dividends are the most common type. The decision to issue dividends is
typically made by the board of directors, taking into account the
company's operating needs for a given financial year. When a dividend is
announced, it has an impact on the financial statements of a company.
Resultantly, dividend announcements create a liability which impacts the
balance sheet by increasing the current liabilities and decreases
shareholder equity, specifically retained earnings, on the balance Baker
\& Powell (\protect\hyperlink{ref-baker2009understanding}{2009: 374}).
In other words, the company incurs an obligation to pay out the
dividend, and the value of the company retained by shareholders
decreases accordingly. From this when can conclude that dividends are
catergorized as a capital budgeting decision and indirectly implies that
investors could infer about management quality overtime by studying
dividend yield. Management quality here refers to cash flow management
and management skill in identifying and monetizing investment
opportunities. Therefore,considering the dividend yield equation below
and assuming that the dividend payout ratio (DPR) is constant we notice
that dividend yield (DY) becomes a function of the earnings
yield(EPS/Price). Figure 1, shows the 12 month net trailing dividend
yield of Standard Bank relative to the log of theprice since 2010. It
shows the clear and expected negative correlation between DY and price
over time (during a period where the dividend per share payment
increased at best uniformly and moderately. Since value investing is
concerned with identifying stocks that are priced below their market
value, studies that confirm the existence of dividend signalling
predicting power of returns validate that the existence of a value
signal and dividends can be used as a proxy. \[
DY=EPS/Price*DPR
\]

Cash dividends, although widely used, are not as tax-efficient as other
types of capital distributions, such as share buybacks or stock
repurchases. In this form of capital redistribution, a firm exchanges
assets for outstanding shares, which shrinks the company's assets by the
amount of cash paid out. This action too reduces both its borrowing base
and the shareholders' aggregate equity Baker \& Powell
(\protect\hyperlink{ref-baker2009understanding}{2009: 429}). A clear
benefit to the company is that it is more flexible when compared to the
rigid dividend payout structures. To most higher net worth investors,
tax benefits in the form of lower capital gains taxes result in greater
preference for sharebuybacks. It is thus no surprise that this form of
earnings redistribution has gained traction in some advanced economies
such as the US (with the Financial Times recently reporting that
announced stock buybacks in the US reached an all time high of \$437
billion in 2018). Surprisingly, their adoption has been relatively slow
in some emerging economies. According to a study by Wesson, Muller \&
Ward (\protect\hyperlink{ref-wesson2014market}{2014}), there were only
195 open market share repurchases announced in South Africa from 1999 to
2009. In comparison, Manconi, Peyer \& Vermaelen
(\protect\hyperlink{ref-manconi2014buybacks}{2014}) estimated that share
repurchases constituted approximately 58\% of total announcements in the
United States, 15\% in Canada, and 11\% in Japan over the same period,
indicative of a significant disparity in the adoption of share buybacks
across the world, despite their popularity in the United States.

The logical question then is why do firms pay dividends? Miller \& Rock
(\protect\hyperlink{ref-miller1985dividend}{1985}) opines that dividends
are irrelevant (MM theory), he argues that shareholders are indifferent
to dividend payments, implying that there is no optimal dividend policy.
Following this school of thought implies that all dividend policies are
equally good and thus payments of dividends could easily be reinvested
in shares and make no difference to share holder wealth. However, the MM
theorem fails to consider real-world market imperfections that may give
relevance to dividend payments. Considering these constraints the
dividend puzzle gives an interesting take on its relevance and
irrelevance, suggesting that dividends reduce equity value and make
investors worse off Black
(\protect\hyperlink{ref-black1996dividend}{1996}). However, dividends
can be seen as a reward to investors who bear the risk associated with
their investments. Also, dividends can be considered a return on
investment rather than relying solely on capital gains Black
(\protect\hyperlink{ref-black1996dividend}{1996}). Various literature
has emerged trying to solve the puzzel, either supporting irrelevance or
relevance in dividend payments.

Global assets market face multiple constraints or imperfections namely
transaction costs (e.g., taxes and flotation costs), information
asymmetry, and principal-agent problems Baker \& Powell
(\protect\hyperlink{ref-baker2009understanding}{2009}). Taxes play a
role in the argument for dividend relevance. Different investors may be
attracted to different stocks based on their tax treatments, thus
investors choose stocks based on their individual investment needs Van
Deventer, Imai \& Mesler (\protect\hyperlink{ref-van2013advanced}{2013})
Baker \& Powell (\protect\hyperlink{ref-baker2009understanding}{2009}).
However, supporters of the MM theorem argue that changes in dividend
policy should not significantly impact stock prices due to the
substitution effect. According to this effect, allocation decisions of
firms occur almost simultaneously, resulting in a net zero effect on
prices {[}baker2009understanding{]}. Flotation costs refer to the
opportunity costs incurred by a firm when paying dividends. By
distributing dividends, companies forego opportunities to expand their
operations using retained earnings. In a world without flotation costs,
as suggested by the MM theorem, management would be indifferent between
issuing dividends and borrowing from the market. However, in reality,
external financing comes at a higher cost, leading to trade-offs in
dividend policy decisions.

Information asymmetry between shareholders and managers is another
factor that gives relevance to dividend payments. Managers of businesses
typically have greater knowledge of operations thus value of a business
at any given point more than shareholders. As such, investors rely on
dividend announcements to assess a company's valuation. Dividend
signaling conveys information about the company's quality Al-Najjar \&
Kilincarslan (\protect\hyperlink{ref-al2018revisiting}{2018}) and Baker
\& Powell (\protect\hyperlink{ref-baker1999corporate}{1999}). Investors
compare dividend announcements to historical levels while considering
company fundamentals. However, there is a risk of manipulation by
management, making the dividend signal imperfect for determining share
prices. Extending the argument on information asymmetry leads to the
principal-agent problem, where management and shareholders may have
differing goals for the use of retained earnings, leading to conflict
{[}baker2009understanding{]}. The free cash flow hypothesis suggests
that dividend payments force management to raise capital from external
sources, which increases borrowing costs and scrutiny from capital
markets. This, in turn, reduces management's ability to make sub optimal
investments {[}baker2009understanding{]}.

Dividend payments and growth in dividends provides a return cue and over
the years studies on dividend signaling can be categorized into academic
return signaling studies and practitioner-oriented long-term return
studies. Academic studies, such as Fama \& French
(\protect\hyperlink{ref-fama1988permanent}{1988}), found a positive
correlation between increasing predictive power and longer forecast
horizons. However, subsequent studies like Ang \& Bekaert
(\protect\hyperlink{ref-ang2007stock}{2007}) found no evidence of
long-term predictability in stock returns when considering finite sample
influence. This suggests that dividend yield may not be a reliable
predictor of subsequent returns. One possible reason for this declining
predictive power is the increasing use of share buybacks as an
alternative means for capital distribution, which reduces the
contribution of dividend yield to total return
(\protect\hyperlink{ref-robertson2006dividends}{\textbf{robertson2006dividends?}}).

On the other hand, practitioner-oriented literature focuses on the
long-term returns of systematic dividend portfolios. One popular
strategy is the ``Dogs of the Dow (DOD),'' which involves constructing a
portfolio of the top 10 highest-paying dividend stocks on the Dow Jones
Industrial Index at the beginning of the year based on the dividends
paid in the previous 12 months, therefore this entail deploying a high
yield strategy. The most common methodology used in The portfolio is
held for 12 months, and the process is repeated annually. Various
studies have examined the DOD strategy or similar high-yield dividend
strategies in different time periods and regions, consistently showing
superior risk-adjusted returns compared to the market index. Examples of
such studies include Lemmon \& Nguyen
(\protect\hyperlink{ref-lemmon2015dividend}{2015}) in Hong Kong,
Brzeszczyński \& Gajdka
(\protect\hyperlink{ref-brzeszczynski2007dividend}{2007}) in Poland,
Visscher \& Filbeck (\protect\hyperlink{ref-visscher2003dividend}{2003})
in Canada, Filbeck \& Visscher
(\protect\hyperlink{ref-filbeck1997}{1997}) in Britian, and Wang,
Larsen, Ainina, Akhbari \& Gressis
(\protect\hyperlink{ref-wang2011dogs}{2011}) in China. More recently,
Filbeck, Holzhauer \& Zhao
(\protect\hyperlink{ref-filbeck2017dividend}{2017}) investigated the
performance of DOD against a high-yield portfolio of Fortune Most
Desired Companies (MAC) compared to the Dow Jones Industrial Average and
the S\&P 500. The study found significantly higher risk-adjusted returns
for the DOD strategy.

\newpage
\begin{longtable}{rllll}
\caption*{
{\large Global Dividend Portfolio Signalling Results}
} \\ 
\toprule
Year & Author & Geography & Signal & Result \\ 
\midrule
1997 & Filbeck & United Kingdom & High Dividend Yield & Outperformed market index \\ 
2001 & Da Silva & Brazil & High Dividend Yield & Outperformed market index \\ 
2003 & Visscher and Filbeck & Canada & Dividend Growth & Outperformed market index \\ 
2007 & Brzeszczyński & Poland & Dividend Growth & Outperformed market index \\ 
2007 & Fama and Eugene & US & High Dividend Yield & Outperformed market index \\ 
2011 & Wang et al & China & High Dividend Yield & Outperformed market index \\ 
2011 & Rennie & Optimiization & High Dividend Yield & Outperformed market index \\ 
2015 & Lemmon & Hong Kong & High Dividend Yield & Outperformed market index \\ 
2017 & Filbeck & US & High Dividend Yield & Outperformed market index \\ 
2017 & You & Taiwan & High Dividend Yield & Outperformed market index \\ 
\bottomrule
\end{longtable}

\newpage

\hypertarget{methodology}{%
\section{Methodology}\label{methodology}}

\hypertarget{tax-considerations}{%
\subsection{Tax considerations}\label{tax-considerations}}

Portfolio theory was developed in a perfect world without friction. In
practice, frictions need to be considered and in portfolio construction
this often entails considering the effect of taxes on income and capital
gains as they can erode returns and significantly alter risks and return
characteristics of shares. The contribution of dividends and capital
gains to total return can lead to varying tax efficiencies for shares as
most jurisdictions imposed higher taxes than on capital gains. Therefore
shares with higher contribution of dividends will be less tax efficient
than those with a higher capital gains component and with timing most
jurisdictions tax dividends in the year that they are received\^{}\{See
Deloitte's tax guides and country highlights:
\url{https://dits.deloitte.com/\#TaxGuides}\}.

Jurisdictional laws can also affect the distribution of taxable returns
amongst shares depending on their class namely ordinary shares or
preferred shares. Preferred shares are viewed as a substitute for bonds
and income from preferred shares are often given tax at a lower rate
than those from dividends from ordinary shares.

We will not survey global tax regimes or incorporate all potential tax
complexities into the portfolio construction but assume a high level
commonalities exists amongst all jurisdictions this study uses. This is
a resonable assumption considering the summary of taxes on dividends and
capital gains from major economies. For simplicity, we will assume a
basic tax regime includes the key elements of investment-related taxes
that are representative of what a typical taxable asset owner of a
global portfolio will contend with. The proposed methodology to employ
on the dividend portfolios use the following methodology.

\[
r_{a t}=p_d r_{p t}\left(1-t_d\right)+p_a r_{p t}\left(1-t_{c g}\right)
\] where \(r_{a t}\) the after tax return, \(p_d=\) the proportion of
\(r_{p t}\) attributed to dividend income, \(p_a=\) the proportion of
\(r_{p t}\) attributed to price appreciation, \(t_d=\) the dividend tax
rate and \(t_{c g}=\) the capital gains tax rate

\newpage

\hypertarget{portfolio-construction}{%
\subsection{Portfolio Construction}\label{portfolio-construction}}

First, we rebalance at the end of March and September and construct
fully invested, long only portfolios. On each re balancing date, we
first take the top 100 stocks by market capitalization (MC), and then
select the top quintile (20 stocks) based on the relevant signal scores
. We then apply 25bps trading costs to both buying and selling of
stocks, and (where applicable) replace delisted stocks with cash.

We will then use total return values, adjust for stock splits and other
distorting effects on prices to calculate portfolio returns. We also
carefully apply back-dated adjustments to dividends paid to accurately
arrive at on-the-day dividends and actual closing prices when
calculating our Dividend Yield and Dividend Per Share Growth measures.

We also apply at each rebalancing several portfolio optimization
routines (minimum variance, equal risk contribution (ERC), mean-variance
and max diversification measures. The optimizations are constrained to
have minimum and maximum weight exposure of 0.5 and 1.5 times the equal
weighted alternative.With our quintile portfolios, this implies weights
ranging between 2.5\% and 7.5\%.

Following this we will construct back-tests on the subset of local data
for the choose dividend signal portfolios. The factor portfolios
considered are as follows

\newpage

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-al2018revisiting}{}}%
Al-Najjar, B. \& Kilincarslan, E. 2018. Revisiting firm-specific
determinants of dividend policy: Evidence from turkey. \emph{Economic
issues}. 23(1):3--34.

\leavevmode\vadjust pre{\hypertarget{ref-ang2007stock}{}}%
Ang, A. \& Bekaert, G. 2007. Stock return predictability: Is it there?
\emph{The Review of Financial Studies}. 20(3):651--707.

\leavevmode\vadjust pre{\hypertarget{ref-baker2009understanding}{}}%
Baker, H.K. \& Powell, G. 2009. \emph{Understanding financial
management: A practical guide}. John Wiley \& Sons.

\leavevmode\vadjust pre{\hypertarget{ref-baker1999corporate}{}}%
Baker, H.K. \& Powell, G.E. 1999. How corporate managers view dividend
policy. \emph{Quarterly Journal of Business and Economics}. 17--35.

\leavevmode\vadjust pre{\hypertarget{ref-bhattacharyya2007dividend}{}}%
Bhattacharyya, N. 2007. Dividend policy: A review. \emph{Managerial
Finance}. 33(1):4--13.

\leavevmode\vadjust pre{\hypertarget{ref-black1996dividend}{}}%
Black, F. 1996. The dividend puzzle. \emph{Journal of Portfolio
Management}. 8.

\leavevmode\vadjust pre{\hypertarget{ref-brzeszczynski2007dividend}{}}%
Brzeszczyński, J. \& Gajdka, J. 2007. Dividend-driven trading
strategies: Evidence from the warsaw stock exchange. \emph{International
Advances in Economic Research}. 13:285--300.

\leavevmode\vadjust pre{\hypertarget{ref-cornell2014dividend}{}}%
Cornell, B. 2014. Dividend-price ratios and stock returns: International
evidence. \emph{Journal of Portfolio management}. 40(2):122.

\leavevmode\vadjust pre{\hypertarget{ref-deangelo2006irrelevance}{}}%
DeAngelo, H. \& DeAngelo, L. 2006. The irrelevance of the MM dividend
irrelevance theorem. \emph{Journal of financial economics}.
79(2):293--315.

\leavevmode\vadjust pre{\hypertarget{ref-fama1988permanent}{}}%
Fama, E.F. \& French, K.R. 1988. Permanent and temporary components of
stock prices. \emph{Journal of political Economy}. 96(2):246--273.

\leavevmode\vadjust pre{\hypertarget{ref-filbeck1997}{}}%
Filbeck, G. \& Visscher, S. 1997. Dividend yield strategies in the
british stock market. \emph{The European Journal of Finance}.
3(4):277--289.

\leavevmode\vadjust pre{\hypertarget{ref-filbeck2017dividend}{}}%
Filbeck, G., Holzhauer, H.M. \& Zhao, X. 2017. Dividend-yield
strategies: A new breed of dogs. \emph{The Journal of Investing}.
26(2):26--47.

\leavevmode\vadjust pre{\hypertarget{ref-gordon1963optimal}{}}%
Gordon, M.J. 1963. Optimal investment and financing policy. \emph{The
Journal of finance}. 18(2):264--272.

\leavevmode\vadjust pre{\hypertarget{ref-hussainey2011dividend}{}}%
Hussainey, K., Mgbame, C.O. \& Chijoke-Mgbame, A.M. 2011. Dividend
policy and share price volatility: UK evidence. \emph{The Journal of
risk finance}. 12(1):57--68.

\leavevmode\vadjust pre{\hypertarget{ref-jensen1976theory}{}}%
Jensen, M.C. \& Meckling, W.H. 1976. Theory of the firm: Managerial
behavior, agency costs and ownership structure. \emph{Journal of
financial economics}. 3(4):305--360.

\leavevmode\vadjust pre{\hypertarget{ref-10.2307ux2f3694818}{}}%
Koch, A.S. \& Sun, A.X. 2004. Dividend changes and the persistence of
past earnings changes. \emph{The Journal of Finance}. 59(5):2093--2116.

\leavevmode\vadjust pre{\hypertarget{ref-lemmon2015dividend}{}}%
Lemmon, M.L. \& Nguyen, T. 2015. Dividend yields and stock returns in
hong kong. \emph{Managerial Finance}. 41(2):164--181.

\leavevmode\vadjust pre{\hypertarget{ref-lintner1956distribution}{}}%
Lintner, J. 1956. Distribution of incomes of corporations among
dividends, retained earnings, and taxes. \emph{The American economic
review}. 46(2):97--113.

\leavevmode\vadjust pre{\hypertarget{ref-maio2015dividend}{}}%
Maio, P. \& Santa-Clara, P. 2015. Dividend yields, dividend growth, and
return predictability in the cross section of stocks. \emph{Journal of
Financial and Quantitative Analysis}. 50(1-2):33--60.

\leavevmode\vadjust pre{\hypertarget{ref-manconi2014buybacks}{}}%
Manconi, A., Peyer, U. \& Vermaelen, T. 2014. Buybacks around the world.
\emph{European Corporate Governance Institute (ECGI)-Finance Working
Paper}. 436.

\leavevmode\vadjust pre{\hypertarget{ref-masum2014dividend}{}}%
Masum, A. 2014. Dividend policy and its impact on stock price--a study
on commercial banks listed in dhaka stock exchange. \emph{Global
disclosure of Economics and Business}. 3(1).

\leavevmode\vadjust pre{\hypertarget{ref-miller1985dividend}{}}%
Miller, M.H. \& Rock, K. 1985. Dividend policy under asymmetric
information. \emph{The Journal of finance}. 40(4):1031--1051.

\leavevmode\vadjust pre{\hypertarget{ref-rangvid2014dividend}{}}%
Rangvid, J., Schmeling, M. \& Schrimpf, A. n.d. Dividend predictability
around the world. \emph{Journal of Financial and Quantitative Analysis}.
49(5-6):1255--1277.

\leavevmode\vadjust pre{\hypertarget{ref-robertson2006}{}}%
Robertson, D. \& Wright, S. 2006. Dividends, total cash flow to
shareholders, and predictive return regressions. \emph{Review of
Economics and Statistics}. 88(1):91--99.

\leavevmode\vadjust pre{\hypertarget{ref-suwanna2012impacts}{}}%
Suwanna, T. 2012. Impacts of dividend announcement on stock return.
\emph{Procedia-Social and Behavioral Sciences}. 40:721--725.

\leavevmode\vadjust pre{\hypertarget{ref-van2013advanced}{}}%
Van Deventer, D.R., Imai, K. \& Mesler, M. 2013. \emph{Advanced
financial risk management: Tools and techniques for integrated credit
risk and interest rate risk management}. John Wiley \& Sons.

\leavevmode\vadjust pre{\hypertarget{ref-vijayakumar2010effect}{}}%
Vijayakumar, A. 2010. Effect of financial performance on share prices in
the indian corporate sector: An empirical study. \emph{Management and
Labour Studies}. 35(3):369--381.

\leavevmode\vadjust pre{\hypertarget{ref-visscher2003dividend}{}}%
Visscher, S. \& Filbeck, G. 2003. Dividend-yield strategies in the
canadian stock market. \emph{Financial Analysts Journal}. 59(1):99--106.

\leavevmode\vadjust pre{\hypertarget{ref-wang2011dogs}{}}%
Wang, C., Larsen, J.E., Ainina, M.F., Akhbari, M.L. \& Gressis, N. 2011.
The dogs of the dow in china. \emph{International Journal of Business
and Social Science}. 2(18).

\leavevmode\vadjust pre{\hypertarget{ref-wesson2014market}{}}%
Wesson, N., Muller, C. \& Ward, M. 2014. Market underreaction to open
market share repurchases on the JSE. \emph{South African Journal of
Business Management}. 45(4):59--69.

\end{CSLReferences}

\bibliography{Tex/ref}





\end{document}
