---
output:
  md_document:
    variant: markdown_github
---
# Cleaning 

self explanotory, but incase you change the dataset be mindful of the number of columns and change in the names accordingly. 
```{r}
# loadings
pacman::p_load("xts", "tidyverse", "tbl2xts", "PerformanceAnalytics", 
               "lubridate", "glue", "zoo")

df <- readxl::read_xlsx("data/MAD .xlsx")

#  change the column names for ease of analysis

geographical_codenames <- c("UK_HY", "EM_HY", "UK", "EM", "UK_HY_B", "UK_B", "JP_HY", "EU", "US_HY", "US", "W_HY", "W", "EU_DG", "EU_2", "JP_DG", "US_DG", "US_2", "JP", "SA_DG", "SA", "SA_HY", "EU_HY")

colnames(df)[2:23] <- geographical_codenames

```

# Purpose

We want to investigate the performance of dividend paying portfolios across different regions. We look at index construction,  dynamic performance measures and risk analysis of these portfolios. in essence, why do these portfolios work or not and when they seem to add value to a portfolio. We also high the distinction in growth versus HY performance. 

Diversification, Return and Risk (Sd and MaxDrawdowns) and a combination of the two. 

# Objective

Provide an analysis into dividend portfolios. Literature has shown that they provide greater excess return over time versus the s&p because the dividend component over and above the capital gains. We expand this to other indices, FTSE, MSCI. 

- So its risk and return that we need to evaluate, so do they provide that excess return over time that is significantly better than its parent index. 

- If they do what are the drivers, we note the construction of the indexes by the different providers. 
are they exposed to higher risk assets. lets mention the composition of different sectors in the index. are some sectors prone to paying higher dividend than others and what is the relationship between return and dividend paynig stock. 

- if they do provide more return do they give more risk. what measure of risk can we give to illustrate this and how do these indexes cover against these risks of the value trap. What other measures of risk will be important to measure over time for these portfolios in the various regions. Mentioning the correlations to market is important 

- finally we consider south African portfolios, are they able to consistently give a return. Lets use the sharpe ratios to determine the consistency of the portfolios. 

- Show the trailing performances in one graph, ie 2, 3, 5, 10 and since inception. 
# Instruments 

Dividend portfolios are usually constructed using either a high yeild or a growth in dividend signal. 


##  Compounding Returns, Aggregate effects of Portfolios

I calculate excess returns as the monthly difference return for index and benchmark, then geometrically chain the excess return to compute the cumulative excess returns. The indices across regions have different inception dates therefore not purely comparable across regions. To correct for this we start the series will start from the first date for all indices and standardized to 1, ie all indices start from the same point. However these indices are not purely comparable, inceptions date may lead to differing momentum effects.

With that caveat, lets start the analysis.


```{r echo=TRUE, message=FALSE, warning=FALSE}
source("code/simpleexcessreturn.R")
source("code/EXCESSRETURN.R")
library(glue)
library(stats)

#   calculate simple returns just simple excess returns
a <- df %>% MY_excess_return(., "UK_HY", "UK") 
b <- df %>% MY_excess_return(., "UK_HY_B", "UK_B")

c <- df %>% MY_excess_return(., "US_HY", "US")
d <- df %>% MY_excess_return(., "US_DG", "US_2")

e <- df %>% MY_excess_return(., "EU_HY", "EU")
f <- df %>% MY_excess_return(., "EU_DG", "EU_2")

g <- df %>% MY_excess_return(., "JP_HY", "JP")
h <- df %>% MY_excess_return(., "JP_DG", "JP")

i <- df %>% MY_excess_return(., "EM_HY", "EM")

j <- df %>% MY_excess_return(., "SA_HY", "SA")
k <- df %>% MY_excess_return(., "SA_DG", "SA")

# Table to describe excess returns


excess_return_df <- list( a, b, c, d, e,f,g,h,i,j,k) %>%
  reduce(inner_join, by='date')

table_df <- excess_return_df %>% 
  gather(Regions, Cumulative_Excess_Return, -date) %>% 
  group_by(Regions) %>% 
  summarise("Start Date" = first(date) , "Total Years"  = round( n()/12,0),  Median = median(Cumulative_Excess_Return),  "Cumulative Excess Return" = last(Cumulative_Excess_Return))

#  we notice that growth portfolios dont add signifiant value, SA offers similar to HY and DG. Whats the reason? HY did good in most advanced market economies. Gving more than 1X in excess cumulatively, the best being UK assets high yeild. EM not so well on a cumulative basis
```

## Stratification 

Next I stratifying the sample period between periods of different market cycles and volatility. 

For volatility I will use the historical series for the CBOE VIX index in the US, V2 X in the euro, and JALSH VR for SA. EM market volatility will be proxies by the VIX index. I will get the rolling standard deviation bucket the data two in either low, mid or high vol. 

After stratification, chain the excess returns for the different periods before annualizing. This ensures that we can compare performance according to different periods. 

- Make sure to separate according to region tables accroding to region. 
- State the geometic mean and median for the return and include the compounding periods

- for somereason dates are not at monthend 
```{r echo=TRUE, message=FALSE, warning=FALSE}
#   get the vol data and get some dates

 vol_data <- readxl::read_xlsx("data/volatility.xlsx")
 VIX <- vol_data %>% select(Date, VIX)
 V2X <- vol_data %>% select(Date, V2X)
 JSV <- vol_data %>% select(Date, JALSHVOL)
# get rolling sd for the volatility index 

 source("code/rollingstarnddev.R")

# US 

 Vixroll <- Rolling_sd(VIX ,"VIX")
# 
# # get the top quartile and bottom quartil
# 
 strat_df <- Vixroll %>% mutate(topQ = quantile(RollSD, probs = 0.8), 
               botQ = quantile(RollSD, probs = 0.2),
               Strat = ifelse(RollSD >= topQ, "HiVol", 
                           ifelse(RollSD <= botQ, "LowVol", "Normal_Vol")))
 
# # US strat
 
 hivol_per_vector_us <- strat_df %>% filter(Strat %in% "HiVol") %>% pull(Date)
 lovol_per_vector_us <- strat_df %>% filter(Strat %in% "LowVol") %>% pull(Date)
# 
# # Europe strat 
# 
 Vixroll <- Rolling_sd(V2X ,"V2X")
# get the top quartile and bottom quartil

 strat_df <- Vixroll %>% mutate(topQ = quantile(RollSD, probs = 0.8), 
               botQ = quantile(RollSD, probs = 0.2),
              Strat = ifelse(RollSD >= topQ, "HiVol", 
                          ifelse(RollSD <= botQ, "LowVol", "Normal_Vol")))
# 
 hivol_per_vector_eu  <- strat_df %>% filter(Strat %in% "HiVol") %>% pull(Date)
 lovol_per_vector_eu  <- strat_df %>% filter(Strat %in% "LowVol") %>% pull(Date)
# 
# # SA 
# 
 Vixroll <- Rolling_sd(JSV ,"JALSHVOL")
# 
# # get the top quartile and bottom quartil
# 
 strat_df <- Vixroll %>% mutate(topQ = quantile(RollSD, probs = 0.8), 
               botQ = quantile(RollSD, probs = 0.2),
               Strat = ifelse(RollSD >= topQ, "HiVol", 
                           ifelse(RollSD <= botQ, "LowVol", "Normal_Vol")))
# 
 hivol_per_vector_sa <- strat_df %>% filter(Strat %in% "HiVol") %>% pull(Date)
 lovol_per_vector_sa <- strat_df %>% filter(Strat %in% "LowVol") %>% pull(Date)

 
 # Getting excess return for the period and indices 
 #  High Vol df 
 
source("code/Stratifier.R")
  
Hivol_performance <-  bind_rows(
 stratifier(df, "EU_HY", "EU", hivol_per_vector_eu, "High Vol Period" ),
 stratifier(df, "EU_DG", "EU_2", hivol_per_vector_eu, "High Vol Period" ),
 stratifier(df, "UK_HY", "UK", hivol_per_vector_eu, "High Vol Period" ),
 stratifier(df, "UK_HY_B", "UK", hivol_per_vector_eu, "High Vol Period" ),
 stratifier(df, "JP_HY", "JP", hivol_per_vector_us, "High Vol Period" ),
 stratifier(df, "JP_DG", "JP", hivol_per_vector_us, "High Vol Period" ),
 stratifier(df, "EM_HY", "EM", hivol_per_vector_us, "High Vol Period" ),
 stratifier(df, "SA_HY", "SA", hivol_per_vector_sa, "High Vol Period" ),
 stratifier(df, "SA_DG", "SA", hivol_per_vector_sa, "High Vol Period" ),
 stratifier(df, "US_HY", "US", hivol_per_vector_us, "High Vol Period" ), 
 stratifier(df, "US_DG", "US", hivol_per_vector_us, "High Vol Period" )
 )

#  Low Vol df
Lovol_performance <-  bind_rows(
 stratifier(df, "EU_HY", "EU", lovol_per_vector_eu, "Low Vol Period" ),
 stratifier(df, "EU_DG", "EU_2", lovol_per_vector_eu, "Low Vol Period" ),
 stratifier(df, "UK_HY", "UK", lovol_per_vector_eu, "Low Vol Period" ),
 stratifier(df, "UK_HY_B", "UK", lovol_per_vector_eu, "Low Vol Period" ),
 stratifier(df, "JP_HY", "JP", lovol_per_vector_us, "Low Vol Period" ),
 stratifier(df, "JP_DG", "JP", lovol_per_vector_us, "Low Vol Period" ),
 stratifier(df, "EM_HY", "EM", lovol_per_vector_us, "Low Vol Period" ),
 stratifier(df, "SA_HY", "SA", lovol_per_vector_sa, "Low Vol Period" ),
 stratifier(df, "SA_DG", "SA", lovol_per_vector_sa, "Low Vol Period" ),
 stratifier(df, "US_HY", "US", lovol_per_vector_us, "Low Vol Period" ), 
 stratifier(df, "US_DG", "US", lovol_per_vector_us, "Low Vol Period" )
 )
 
```


# Interest rate cycles

Given a series of central bank interest rates. I want to get dates of n consecutive interest rate changes. 

-  I will create a column that conditions if there was a rate change or nt.
-  if there has been a change for more than 4 quarters take the date. 

Can I seggregate the hiking and cutting cycles using the one inrest rate data series from the US. 

## notes 

- SA doesn't enough "periods" for cutting 


```{r}
#   get the vol data and get some dates

rate_data <- readxl::read_xlsx("data/Interest Rates.xlsx") 

US <- rate_data %>% select(Date, US) %>% arrange(Date)

# Get Rates for the US
source("code/Interest_Regime.R")
 
Regime_change_df(US, 3)
#  filter to get the vectors
Hiking_date_vector <- Regime_df %>% filter(regime %in% "Hiking") %>% pull(Date)
Cutting_date_vector <- Regime_df %>% filter(regime %in% "Cutting") %>% pull(Date)
Neutral_date_vector <- Regime_df %>% filter(regime %in% "Neutral") %>% pull(Date) 

# Hiking Performance

Hiking_performance <-  bind_rows(
 stratifier(df, "EU_HY", "EU", Hiking_date_vector, "Hiking" ),
 stratifier(df, "EU_DG", "EU_2", Hiking_date_vector, "Hiking" ),
 stratifier(df, "UK_HY", "UK", Hiking_date_vector, "Hiking" ),
 stratifier(df, "UK_HY_B", "UK", Hiking_date_vector, "Hiking" ),
 stratifier(df, "JP_HY", "JP", Hiking_date_vector, "Hiking" ),
 stratifier(df, "JP_DG", "JP", Hiking_date_vector, "Hiking" ),
 stratifier(df, "EM_HY", "EM", Hiking_date_vector, "Hiking"),
 stratifier(df, "SA_HY", "SA", Hiking_date_vector, "Hiking" ),
 stratifier(df, "SA_DG", "SA", Hiking_date_vector, "Hiking" ),
 stratifier(df, "US_HY", "US", Hiking_date_vector, "Hiking" ), 
 stratifier(df, "US_DG", "US", Hiking_date_vector, "Hiking" )
 )

#  Cutting Perfromance

Cutting_performance <-  bind_rows(
 stratifier(df, "EU_HY", "EU", Cutting_date_vector, "Cut" ),
 stratifier(df, "EU_DG", "EU_2", Cutting_date_vector, "Cut" ),
 stratifier(df, "UK_HY", "UK", Cutting_date_vector, "Cut" ),
 stratifier(df, "UK_HY_B", "UK", Cutting_date_vector, "Cut" ),
 stratifier(df, "JP_HY", "JP", Cutting_date_vector, "Cut" ),
 stratifier(df, "JP_DG", "JP", Cutting_date_vector, "Cut" ),
 stratifier(df, "EM_HY", "EM", Cutting_date_vector, "Cut"),
 stratifier(df, "SA_HY", "SA", Cutting_date_vector, "Cut" ),
 stratifier(df, "SA_DG", "SA", Cutting_date_vector, "Cut" ),
 stratifier(df, "US_HY", "US", Cutting_date_vector, "Cut" ), 
 stratifier(df, "US_DG", "US", Cutting_date_vector, "Cut" )
 )

# Nuetral 

Nuetral_perfromance <-  bind_rows(
 stratifier(df, "EU_HY", "EU", Neutral_date_vector, "Neutral" ),
 stratifier(df, "EU_DG", "EU_2", Neutral_date_vector, "Neutral" ),
 stratifier(df, "UK_HY", "UK", Neutral_date_vector, "Neutral" ),
 stratifier(df, "UK_HY_B", "UK", Neutral_date_vector, "Neutral" ),
 stratifier(df, "JP_HY", "JP", Neutral_date_vector, "Neutral" ),
 stratifier(df, "JP_DG", "JP", Neutral_date_vector, "Neutral" ),
 stratifier(df, "EM_HY", "EM", Neutral_date_vector, "Neutral"),
 stratifier(df, "SA_HY", "SA", Neutral_date_vector, "Neutral" ),
 stratifier(df, "SA_DG", "SA", Neutral_date_vector, "Neutral" ),
 stratifier(df, "US_HY", "US", Neutral_date_vector, "Neutral" ), 
 stratifier(df, "US_DG", "US", Neutral_date_vector, "Neutral" )
 )
```


# rolling consistency in returns

on a rolling basis i want to find out how much bang for buck is offered by dividend portfolios 
, and more importantly discover how consistent the returns for a given strategy are

to do this we will first 

- calculate the returns for both benchmark and index and get the tracking error of the each index to its benchmark.
- combine into one table
- then smiply on a rolling basis depict the movement of each pair. 
- we then graph that. 


```{r}
#  source 

source("code/InformationRatioRoll.R")

a <-  df %>% Information_Ratio_Roll(., "EU_HY", "EU", 20100104, 36)
b <-  df %>% Information_Ratio_Roll(., "EU_DG", "EU_2",20100104, 36)
 c <- df %>% Information_Ratio_Roll(., "UK_HY", "UK", 20100104, 36)
 d <- df %>% Information_Ratio_Roll(., "UK_HY_B", "UK", 20100104, 36)
 e <- df %>% Information_Ratio_Roll(., "JP_HY", "JP", 20100104, 36)
 f <- df %>% Information_Ratio_Roll(., "JP_DG", "JP", 20100104, 36)
 g <- df %>% Information_Ratio_Roll(., "EM_HY", "EM", 20100104, 36)
 h <- df %>% Information_Ratio_Roll(., "SA_HY", "SA", 20100104, 36)
 i <- df %>% Information_Ratio_Roll(., "SA_DG", "SA", 20100104, 36)
 j <- df %>% Information_Ratio_Roll(., "US_HY", "US", 20100104, 36)
 k <- df %>% Information_Ratio_Roll(., "US_DG", "US_2", 20100104, 36)

consistency_df <- list(a, b, c, d, e,f,g,h,i,j,k) %>%
  reduce(inner_join, by='date') %>% 
  gather(IR , ret, -date) 
 
plot <- consistency_df %>%   ggplot() + 
geom_line(aes(date, ret), color = "steelblue", size = 1.1, alpha = 0.8) + 
fmxdat::theme_fmx() + 
facet_wrap(~IR) + 
labs(x = "", y = "return", title = "Performance Consistency", subtitle = "Dividend Portfolios not as good as we thought", caption = "Source:Bloomberg and\n Authors Calculations")

plot

```
the results here generally show inconsistent performance of dividend strategies. the information ratio measures performance consistency of a portfolio over its benchmark, a ratio of more than 0 is desirable. most strategies typically in insustry struggle to consisitency deliver risk adjusted return of anything beyond 0.5. The figure above however shows that on a rolling 36 month basis, dividend portfolios be it growth or high yield perform worse that their benchmarks. we assess the performance on a 24, 36 month basis and find similar results. Standing out are EM HY and 

# source of volatility

# Observations

- we have dividend portfolios of HY and DGPS in US, UK, JAPAN, EM and SA. 

## Cumulative returns
- FUDP-UK (HY) had the most impressive

These next two show marginal improvements over market indices
- M2EUGDY-EU (HY) 
- M2GBDY-UK (HY)

Overall a positive excess return does show some gain to harvesting such portfolios. 

## Stratification analysis 

If we just consider the level of volatility in global financial markets. we can see a clear trend. 

- most portfolios give lower returns when in high vol versus low vol 
- except for SPSADAZT-SA (DGPS), TJDIVD-SA(HY), SPDAEET-EU(DGPS) and M2EFDY (HY)-EM.


## Rolling returns 

Overall, massive divergence followed by a convergence in rolling excess returns. There is some divergence towards the end of the sample period. 

- FUDP-UK (HY), SPSADAZT-SA (DGPS), TJDIVD-SA (HY) visually have massive variance in their rolling excess returns. 

- Others don't have erratic movements in rolling returns. 

# Analysis

Dividend portfolios either HY or DGPS have overtime give some level of positive return, as measured by the cumulative return. 
However, HY indexes give above average excess return for the sample period. Overtime however, most portfolios have choppy excess cumulative returns. There is no super convincing signal that these portfolios give some consistent excess return. 

The moment we stratifying according to different periods of volatility we notice that during periods of high volatility, its less the type of signal and more of the region that plays a big part in explaining the performance. in that case emerging market assets perform better than in low volatility environments. Unusual given in this time there is a flight to safety and EM will be risky at this time. During periods of low vol, advanced market portfolios generally give higher returns that in high vol conditions. 

When we consider rolling returns, excess returns for most portfolios move in a similar direction, generally there are part of the same asset class, exposed to the same risk factors and should behave the same way.  with the exception the SA portfolios. we notice that over three years, it has great variance in excess returns. This too can be said about the UK high yield portfolio. 

So what I can pick out is that dividend portfolios in EM behave different from advanced economies. 

To do 
- Will stratifying further, look at mid vol, inflation and interest rates? 

Working on the data section, where i describe the portfolios and their return signalling, 

Looked at cumulative excess return. no clear signal but for two HY portfolios. 
stratification, all portfolios perform as expected 

# Questions and some thoughts 


- mention why it would be better to hold the market portfolios in some instances. there were significant drawdown in certian periods=. this is why the drawdown table would make a lot of sense.

- when it signals negative and positive. 

- there is upside to the high divi-strategies despite thier stringent rules of security inclusion, growth portfolios have significant drawdowns, want to  and dividend growth. is there mean reversion. do they face significant draw-downs, speed of recovery from drawdowns, that may influence changes.  

- inefficeintly high. bsuiness will be high, dont investment in companies with high capex. its gives a signal to the markets tgat management knows its companies are undervalued and that there know something the market doesnt know. 

- it makes sense if comapnies are good actors. 

- expand on the apparent weakness and strengths of divi stratgies. 

- can improve certain financial sratios and those are boosted and do those companies


