---
output:
  md_document:
    variant: markdown_github
---

# Objective

The goal is to assess the performance of dividend yield as an investment strategy. I plan to use optimized portfolios of the highest paying dividend stock and/or highest growth in dividends for a group of assets.

- First calculate the excess returns for indices and their benchmarks
- Explain relationships within the return series for each region with and without stratifying the sample. 
- Then maybe look to build own dividend portfolios to see how that would have performed.

# Instruments 

The global dividend portfolios considered in the table below are sourced from various literature from a practitioner perspective. They represent stylized portfolio constructed from respective market indexes. Using a similar approach I will consider broad market indices that are used to construct the dividend portfolios listed below.

```{r Instruments, echo=FALSE, message=FALSE, warning=FALSE}
library(knitr)
Table_data <- readxl::read_xlsx("data/Systematic Indices and Benchmarks.xlsx")
knitr::kable(Table_data) 
```

##  Excess Return

Excess returns here are calculated as the difference between cumulative index return and benchmark return. 

```{r}
# loadings 

pacman::p_load("xts", "tidyverse", "tbl2xts", "PerformanceAnalytics", 
               "lubridate", "glue")
library(tbl2xts)
library(tidyverse)
library(xts)

source("code/EXCESSRETURN.R")

df <- readxl::read_xlsx("data/MAD .xlsx")
b <- df %>% MY_excess_return(., "GDUEEGF", "M2EFDY")