---
output:
  md_document:
    variant: markdown_github
---

# Objective

The goal is to assess the performance of dividend yield as an investment strategy. I plan to optimize portfolios of the highest paying dividend stock and/or highest growth in dividends for a group of assets.

- First calculate the excess returns for indices and their benchmarks
- Explain relationships within the return series for each region with and without stratifying the sample. 
- Then maybe look to build own dividend portfolios to see how that would have performed.

# Instruments 

The global dividend portfolios considered in the table below are sourced from various literature from a practitioner perspective. They represent stylized portfolio constructed from respective market indexes. 

Using a similar approach I will consider broad market indices that are used to construct the dividend portfolios listed below.

```{r Instruments, echo=FALSE, message=FALSE, warning=FALSE}
library(knitr)
Table_data <- readxl::read_xlsx("data/Systematic Indices and Benchmarks.xlsx")
knitr::kable(Table_data) 
```

##  Excess Return

Excess returns here are calculated as the difference between cumulative index return and benchmark return of several globally traded dividend investment portfolios. All of the indexes considered gross total return and are compared to the performance of the relevant universe benchmark in the same currency.

Cumulative returns are not comparable across different indexes for the different durations. Mind that in the analysis. 

From the results dividend strategies all over the world have been consistently giving a positive premium over the market index. Some indices have been more successful that others, FUDP giving the highest cumulative return amongst all of them.



- consider the mix between high dividend yield versus dividend growth portfolios. 

- make the inception date the same just to get comparability across different markets


```{r echo=FALSE, message=FALSE, warning=FALSE}
# loadings 
pacman::p_load("xts", "tidyverse", "tbl2xts", "PerformanceAnalytics", 
               "lubridate", "glue")
library(tbl2xts)
library(tidyverse)
library(xts)
source("code/EXCESSRETURN.R")
library(quantmod)

df <- readxl::read_xlsx("data/MAD .xlsx") 

# get all permutatation 
A <- df %>% MY_excess_return(.,"FUDP", "TUKXG") 
B <- df %>% MY_excess_return(., "M2EFDY", "GDUEEGF") 
C <- df %>% MY_excess_return(., "M2EUGDY", "GDDUE15X") 
D <- df %>% MY_excess_return(., "M2GBDY", "GDDUUK") 
E <- df %>% MY_excess_return(., "M2JPDY", "TJDIVD") 
F1 <- df %>% MY_excess_return(., "M2USADVD", "GDDUUS") 
G <- df %>% MY_excess_return(., "M2WDHDVD", "GDDUWI") 
H <- df %>% MY_excess_return(., "SPDAEET", "SPTR350E") 
I <- df %>% MY_excess_return(., "SPDAUDT", "SPXT") 
J <- df %>% MY_excess_return(., "SPJXDAJT", "TPXDDVD") 
K <- df %>% MY_excess_return(., "SPSADAZT", "JALSH") 
L <- df %>% MY_excess_return(., "TJDIVD", "JALSH")

joined_df <- bind_cols(A, B, C, D, E, F1, G, H, I, J, K, L) 

compare <- joined_df %>% select(date...1, FUDP, M2EFDY, M2EUGDY, M2GBDY, M2JPDY, M2USADVD, M2WDHDVD, SPDAEET, SPDAUDT, SPJXDAJT, SPSADAZT, TJDIVD) %>% gather(Index , Return , -date...1)

plot <- compare %>% ggplot(aes(x = date...1, y = Return, color = Index)) +
  geom_line() +
  labs(x = "Date", y = "Return", color = "Index") +
  theme_minimal() +
  facet_wrap(~ Index, scales = "free_y", ncol = 4)

plot
```
## Stratification 

If we stratify these samples into different equity market stability cycles, we can then dichipher when these dividend strategies really work. 

```{r}
# retrieve from yahoo
vix <- getSymbols("VIX")

# Turn to tibble 
VIX <- VIX %>%
  tbl2xts::xts_tbl(.)
  
VIX <- VIX %>% select(date, VIX.Close) %>% 
  rename(., close = VIX.Close)
# get rolling volatilty 

RollSD <- VIX %>%  arrange(date) %>%
  mutate(YM = format(date, "%Y-%b")) %>% 
  group_by(YM) %>% 
  mutate(ret = log(close)- lag(log(close))) %>% 
  mutate(ret = coalesce(ret, 0)) %>% 
  mutate(RollSD = RcppRoll::roll_sd(1+ret, 12, fill = NA, align = "right") * 
           sqrt(12)) %>% 
  ungroup() %>% 
  filter(!is.na(RollSD)) %>% 
  select(date, RollSD)
# label and pull dates 
strat_df <- 
  RollSD %>% mutate(topQ = quantile(RollSD, probs = 0.8), 
                botQ = quantile(RollSD, probs = 0.2),
                Strat = ifelse(RollSD >= topQ, "HiVol", 
                               ifelse(RollSD <= botQ, "LowVol", "Normal_Vol")))
#  lets pull dates for the high vol period
hivol_per_vector <- strat_df %>% filter(Strat %in% "HiVol") %>% pull(date)

# use dates to get returns for indexes and benchamrks, I will use the comparison dataframe, that has excess returns to do a crude analysis on excess returns during these periods 

df %>% filter(Date %in% hivol_per_vector) %>% MY_excess_return(.,"FUDP", "TUKXG") 


A <- df %>%filter(Date %in% hivol_per_vector) %>%  MY_excess_return(.,"FUDP", "TUKXG") 
B <- df %>%filter(Date %in% hivol_per_vector) %>%  MY_excess_return(., "M2EFDY", "GDUEEGF") 
C <- df %>% filter(Date %in% hivol_per_vector) %>% MY_excess_return(., "M2EUGDY", "GDDUE15X") 
D <- df %>%filter(Date %in% hivol_per_vector) %>%  MY_excess_return(., "M2GBDY", "GDDUUK") 
E <- df %>%filter(Date %in% hivol_per_vector) %>%  MY_excess_return(., "M2JPDY", "TJDIVD") 
F1 <- df %>%filter(Date %in% hivol_per_vector) %>%  MY_excess_return(., "M2USADVD", "GDDUUS") 
G <- df %>% filter(Date %in% hivol_per_vector) %>% MY_excess_return(., "M2WDHDVD", "GDDUWI") 
H <- df %>% filter(Date %in% hivol_per_vector) %>% MY_excess_return(., "SPDAEET", "SPTR350E") 
I <- df %>%filter(Date %in% hivol_per_vector) %>%  MY_excess_return(., "SPDAUDT", "SPXT") 
J <- df %>%filter(Date %in% hivol_per_vector) %>%  MY_excess_return(., "SPJXDAJT", "TPXDDVD") 
K <- df %>%filter(Date %in% hivol_per_vector) %>%  MY_excess_return(., "SPSADAZT", "JALSH") 
L <- df %>%filter(Date %in% hivol_per_vector) %>%  MY_excess_return(., "TJDIVD", "JALSH")
  
joined_df <- bind_cols(A, B, C, D, E, F1, G, H, I, J, K, L) 

compare <- joined_df %>% select(date...1, FUDP, M2EFDY, M2EUGDY, M2GBDY, M2JPDY, M2USADVD, M2WDHDVD, SPDAEET, SPDAUDT, SPJXDAJT, SPSADAZT, TJDIVD) %>% gather(Index , Return , -date...1)

plot <- compare %>% ggplot(aes(x = date...1, y = Return, color = Index)) +
  geom_line() +
  labs(x = "Date", y = "Return", color = "Index") +
  theme_minimal() +
  facet_wrap(~ Index, scales = "free_y", ncol = 4)

plot 
```


