---
output:
  md_document:
    variant: markdown_github
---
# Goal 

- what is the performance of dividend portfolios. 

- interested in regional performance of indexes that are constrcuted either through HY or DG growth as signals

- the next chunk achieves and now dividend portfolios are proxies for their jurisdiction. 
```{r}
# loadings
pacman::p_load("xts", "tidyverse", "tbl2xts", "PerformanceAnalytics", 
               "lubridate", "glue", "zoo")

df<- readxl::read_xlsx("data/MAD .xlsx")

#  change the column names for ease of analysis

geographical_codenames <- c("UK_HY", "EM_HY", "UK", "EM", "UK_HY_B", "UK_B", "JP_HY", "EU", "US_HY", "US", "W_HY", "W", "EU_DG", "EU_2", "JP_DG", "US_DG", "US_2", "JP", "SA_DG", "SA", "SA_HY", "EU_HY", "W_HY", "W")

colnames(df)[2:23] <- geographical_codenames

```

# Goal and Steps to Acheive them

- Look at aggregate return effects across regions. 
- Stratify by interest rate and market volatility.
- Assess return consistency. 
- and get an idea of risk attributes of constituents - maybe drawdowns could be a tool that we could employ. 

# But first, lets describe what constitutes these indexes

- we need to classify by style what the index offers. There are value, these are stock that trade below their perceived intrinsic value. 

- Next, we consider high yield and growth in dividends per share as our value signals. Why? The indexes we investigate are return oriented factor based strategies, that dividend yield can be either absolute value or growth. 

- HY, are companies that have a history of paying high dividends per share or have dividend yield . if we hold the payout ratio constant, that yield is a function of earnings yield. To achieve that HY status, its either earnings are high or price is low. They are typically in industries such as telecoms and utilities, and REITS (real estate assets) have cash flows that are more steady and predictable, which enables them to distribute a larger dividend. These businesses typically have better-developed business models and depend less on expansion to produce returns. These companies carry high risk of financial distress, because of being part of a value trap. 

- DG, are companies that have experienced, significant grow its dividend distribution. In other words, have seen their dividend yield ratio go up with time. This could be a function of either, the payout ratio, or earnings yield or both.
Companies in this category typically have higher-quality, cash-rich operations that perform well in both up and down markets and can provide excess returns throughout a complete market cycle. There are less likely to experience losses when interest rates are rising.

- Finally we consider total return indexes because it measure the true returns to investors. It factors changes in dividend yield and prices in the index. 

The next table just shows each index and its benchmark, for ease of analysis later.

- The data used is from 20-09-03 to 20-09-23, 20 years because that is the maximum we could retrive for all indexes on Bloomberg. 

```{r}
library(kableExtra)
indexes <- readxl::read_xlsx("data/Index Description.xlsx")

kable(indexes)
```


We want to investigate the performance of dividend paying portfolios across different regions. Firstly we will asess the performance of dividend portfolios over market cycles and interest rate regimes.   dynamic performance measures and risk analysis of these portfolios. in essence, why do these portfolios work or not and when they seem to add value to a portfolio. We also high the distinction in growth versus HY performance. 

So, Return, Risk and a combination of the two (IR) will guide the analysis. 

# Objective

Literature has shown that they provide greater excess return over time versus the s&p because the dividend component over and above the capital gains. We expand this to other indices, FTSE, MSCI and try to pick up 

- So its risk and return that we need to evaluate, so do they provide that excess return over time that is significantly better than its parent index. 

- If they do what are the drivers, we note the construction of the indexes by the different providers. 
are they exposed to higher risk assets. lets mention the composition of different sectors in the index. are some sectors prone to paying higher dividend than others and what is the relationship between return and dividend paynig stock. 

- if they do provide more return do they give more risk. what measure of risk can we give to illustrate this and how do these indexes cover against these risks of the value trap. What other measures of risk will be important to measure over time for these portfolios in the various regions. Mentioning the correlations to market is important 

- finally we consider south African portfolios, are they able to consistently give a return. Lets use the sharpe ratios to determine the consistency of the portfolios. 

- Show the trailing performances in one graph, ie 2, 3, 5, 10 and since inception. 
# Instruments 

Dividend portfolios are usually constructed using either a high yeild or a growth in dividend signal. 


##  Compounding Returns, Aggregate effects of Portfolios

I calculate excess returns as the monthly difference return for index and benchmark, then geometrically chain the excess return to compute the cumulative excess returns. The indices across regions have different inception dates therefore not purely comparable across regions. To correct for this we start the series will start from the first date for all indices and standardized to 1, ie all indices start from the same point. However these indices are not purely comparable, inceptions date may lead to differing momentum effects.

With that caveat, lets start the analysis.


```{r echo=TRUE, message=FALSE, warning=FALSE}
source("code/simpleexcessreturn.R")
source("code/EXCESSRETURN.R")
library(glue)
library(stats)

#   calculate simple returns just simple excess returns
a <- df %>% My_excess_return(., "UK_HY", "UK") 
b <- df %>% My_excess_return(., "UK_HY_B", "UK_B")

c <- df %>% My_excess_return(., "US_HY", "US")
d <- df %>% My_excess_return(., "US_DG", "US_2")

e <- df %>% My_excess_return(., "EU_HY", "EU")
f <- df %>% My_excess_return(., "EU_DG", "EU_2")

g <- df %>% My_excess_return(., "JP_HY", "JP")
h <- df %>% My_excess_return(., "JP_DG", "JP")

i <- df %>% My_excess_return(., "EM_HY", "EM")

j <- df %>% My_excess_return(., "SA_HY", "SA")
k <- df %>% My_excess_return(., "SA_DG", "SA")

l <- df %>% My_excess_return(., "W_HY", "W")


# Table to describe excess returns


excess_return_df <- list( a, b, c, d, e,f,g,h,i,j,k, l) %>%
  reduce(inner_join, by='date')

table_df <- excess_return_df %>% 
  gather(Regions, Cumulative_Excess_Return, -date) %>% 
  group_by(Regions) %>% 
  summarise("Start Date" = first(date) , "Total Years"  = round( n()/12,0),  Median = median(Cumulative_Excess_Return),  "Cumulative Excess Return" = last(Cumulative_Excess_Return))

table_df

#  we notice that growth portfolios dont add signifiant value, SA offers similar to HY and DG. Whats the reason? HY did good in most advanced market economies. Gving more than 1X in excess cumulatively, the best being UK assets high yeild. EM not so well on a cumulative basis
```

## Stratification 

- to get a more nuanced picture of the performance over time, we stratify but first. 

- lets figure out a systematic way to stratifying? For this I do not have a way but I looked at the rolling standard deviation and by eyeballing it saw that meaningful data points are concentrated in the 95th and 5 percentile. 



```{r echo=TRUE, message=FALSE, warning=FALSE}
#   get the vol data and get some dates

 vol_data <- readxl::read_xlsx("data/volatility for indexes.xlsx") %>% gather(index, px , -Date) %>% 
  mutate(ret = px/lag(px)-1, RollSD = RcppRoll::roll_sd(1 + ret, 12, fill = NA, align = "right") * 
             sqrt(12)) %>% 
    filter(!is.na(RollSD))
# plot just to visualize what we are doing
  
vol_plot <- vol_data %>% ggplot()+ 
geom_line(aes(Date, RollSD, color = index))+ 
  facet_wrap(~index)

vol_plot
```


```{r echo=TRUE, message=FALSE, warning=FALSE}
# get rolling sd for the volatility index 

# # get the top quartile and bottom quartil
# 
 strat_df <- vol_data %>% filter(index == "VIX") %>%  mutate(topQ = quantile(RollSD, probs = 0.95), 
               botQ = quantile(RollSD, probs = 0.05),
               Strat = ifelse(RollSD >= topQ, "HiVol", 
                           ifelse(RollSD <= botQ, "LowVol", "Normal_Vol")))
 
# # US strat
 
 hivol_per_vector_us <- strat_df %>% filter(Strat %in% "HiVol") %>% pull(Date)
 lovol_per_vector_us <- strat_df %>% filter(Strat %in% "LowVol") %>% pull(Date)

 # UK 

 strat_df <-vol_data %>% filter(index == "IVIUK") %>% mutate(topQ = quantile(RollSD, probs = 0.95), 
               botQ = quantile(RollSD, probs = 0.5),
              Strat = ifelse(RollSD >= topQ, "HiVol", 
                          ifelse(RollSD <= botQ, "LowVol", "Normal_Vol")))
# 
 hivol_per_vector_uk  <- strat_df %>% filter(Strat %in% "HiVol") %>% pull(Date)
 lovol_per_vector_uk  <- strat_df %>% filter(Strat %in% "LowVol") %>% pull(Date)
#  EU 
 
 strat_df <-vol_data %>% filter(index == "V2X") %>% mutate(topQ = quantile(RollSD, probs = 0.95), 
               botQ = quantile(RollSD, probs = 0.5),
              Strat = ifelse(RollSD >= topQ, "HiVol", 
                          ifelse(RollSD <= botQ, "LowVol", "Normal_Vol")))
# 
 hivol_per_vector_eu  <- strat_df %>% filter(Strat %in% "HiVol") %>% pull(Date)
 lovol_per_vector_eu  <- strat_df %>% filter(Strat %in% "LowVol") %>% pull(Date) 
# # SA 

 strat_df <-vol_data %>% filter(index == "SAVIT40") %>% mutate(topQ = quantile(RollSD, probs = 0.95), 
               botQ = quantile(RollSD, probs = 0.5),
               Strat = ifelse(RollSD >= topQ, "HiVol", 
                           ifelse(RollSD <= botQ, "LowVol", "Normal_Vol")))
# 
 hivol_per_vector_sa <- strat_df %>% filter(Strat %in% "HiVol") %>% pull(Date)
 lovol_per_vector_sa <- strat_df %>% filter(Strat %in% "LowVol") %>% pull(Date)

#  High Vol df 
 
source("code/Stratifier.R")
  
stratifying_df <-  bind_rows(
 stratifier(df, "EU_HY", "EU", hivol_per_vector_eu, "High Vol" ),
 stratifier(df, "EU_DG", "EU_2", hivol_per_vector_eu, "High Vol" ),
 stratifier(df, "UK_HY", "UK", hivol_per_vector_eu, "High Vol" ),
 stratifier(df, "UK_HY_B", "UK", hivol_per_vector_eu, "High Vol"),
 stratifier(df, "JP_HY", "JP", hivol_per_vector_us, "High Vol"),
 stratifier(df, "JP_DG", "JP", hivol_per_vector_us, "High Vol"),
 stratifier(df, "EM_HY", "EM", hivol_per_vector_us, "High Vol"),
 stratifier(df, "SA_HY", "SA", hivol_per_vector_sa, "High Vol"),
 stratifier(df, "SA_DG", "SA", hivol_per_vector_sa, "High Vol"),
 stratifier(df, "US_HY", "US", hivol_per_vector_us, "High Vol"), 
 stratifier(df, "US_DG", "US", hivol_per_vector_us, "High Vol"), 
 stratifier(df , "W_HY", "W", hivol_per_vector_us, "High Vol"), 
 stratifier(df, "EU_HY", "EU", lovol_per_vector_eu, "Low Vol Period" ),
 stratifier(df, "EU_DG", "EU_2", lovol_per_vector_eu, "Low Vol Period" ),
 stratifier(df, "UK_HY", "UK", lovol_per_vector_eu, "Low Vol Period" ),
 stratifier(df, "UK_HY_B", "UK", lovol_per_vector_eu, "Low Vol Period" ),
 stratifier(df, "JP_HY", "JP", lovol_per_vector_us, "Low Vol Period" ),
 stratifier(df, "JP_DG", "JP", lovol_per_vector_us, "Low Vol Period" ),
 stratifier(df, "EM_HY", "EM", lovol_per_vector_us, "Low Vol Period" ),
 stratifier(df, "SA_HY", "SA", lovol_per_vector_sa, "Low Vol Period" ),
 stratifier(df, "SA_DG", "SA", lovol_per_vector_sa, "Low Vol Period" ),
 stratifier(df, "US_HY", "US", lovol_per_vector_us, "Low Vol Period" ), 
 stratifier(df, "US_DG", "US", lovol_per_vector_us, "Low Vol Period" ), 
 stratifier(df, "W_HY", "W", lovol_per_vector_us, "Low Vol Period")
 )

stratifying_df %>% arrange(Name)
```
- we notice that there have been varying lengths in vol periods between geographies. 
- may lead suspicious results in the sense that there may not be enough data points to string good representation of returns
- but general trends for HY indexes.  EM HY > Low Vol. EU_HY> Hi Vol.  JP_HY > Low Vol. SA_HY >High Vol. UK_HY (Both) - Low Vol. US _HY > Low vol and W_HY > Low Vol. 
- and DG . EU_DG > Low vol . JP> High Vol. SA > HI Vol, US > Low_Vol

So typically what characterizes a high vol period and how does that influence our value stock. what main economoic indicators give the most impact in affecting returns? 

# Interest rate cycles

Given a series of central bank interest rates. I want to get dates of n consecutive interest rate changes. 

To do this I will

- create a column that conditions if there was a rate change or nt.
- apply a rolling function that counts a desired number of consistent hikes or cuts or neutral/hold period.
- similar to the vol, aggregate performance in those dates. 

```{r}
rate_data <- readxl::read_xlsx("data/Policy Rates.xlsx") 

names <- c("Date", "US", "UK", "JP", "ECB", "SA")

colnames(rate_data) <- names

US_rates <- rate_data %>% select(Date, US)
UK_rates <- rate_data %>% select(Date, UK)
JP_rates <- rate_data %>% select(Date, JP)
SA_rates <- rate_data %>% select(Date, SA)
ECB_rates <- rate_data %>% select(Date, ECB)
# Get Rates for the US
source("code/Interest_Regime.R")


#  rename the columns for the function to work

Regime_df <- Regime_change_df(US_rates, "US", 5)
Hiking_date_vector_us <- Regime_df %>% filter(regime %in% "Hiking") %>% pull(Date)
Cutting_date_vector_us <- Regime_df %>% filter(regime %in% "Cutting") %>% pull(Date)
Neutral_date_vector_us <- Regime_df %>% filter(regime %in% "Neutral") %>% pull(Date) 

Regime_df <- Regime_change_df(UK_rates, "UK", 5)
Hiking_date_vector_uk <- Regime_df %>% filter(regime %in% "Hiking") %>% pull(Date)
Cutting_date_vector_uk <- Regime_df %>% filter(regime %in% "Cutting") %>% pull(Date)
Neutral_date_vector_uk <- Regime_df %>% filter(regime %in% "Neutral") %>% pull(Date) 

Regime_df <- Regime_change_df(JP_rates, "JP", 5)
Hiking_date_vector_jp <- Regime_df %>% filter(regime %in% "Hiking") %>% pull(Date)
Cutting_date_vector_jp <- Regime_df %>% filter(regime %in% "Cutting") %>% pull(Date)
Neutral_date_vector_jp <- Regime_df %>% filter(regime %in% "Neutral") %>% pull(Date) 

Regime_df <- Regime_change_df(SA_rates, "SA", 5)
Hiking_date_vector_sa <- Regime_df %>% filter(regime %in% "Hiking") %>% pull(Date)
Cutting_date_vector_sa <- Regime_df %>% filter(regime %in% "Cutting") %>% pull(Date)
Neutral_date_vector_sa <- Regime_df %>% filter(regime %in% "Neutral") %>% pull(Date) 

Regime_df <- Regime_change_df(ECB_rates, "ECB", 5)
Hiking_date_vector_eu <- Regime_df %>% filter(regime %in% "Hiking") %>% pull(Date)
Cutting_date_vector_eu <- Regime_df %>% filter(regime %in% "Cutting") %>% pull(Date)
Neutral_date_vector_eu <- Regime_df %>% filter(regime %in% "Neutral") %>% pull(Date) 
# Hiking Performance

Hiking_performance <-  bind_rows(
 stratifier(df, "EU_HY", "EU", Hiking_date_vector_eu, "Hiking" ),
 stratifier(df, "EU_DG", "EU_2", Hiking_date_vector_eu, "Hiking" ),
 stratifier(df, "UK_HY", "UK", Hiking_date_vector_uk, "Hiking" ),
 stratifier(df, "UK_HY_B", "UK", Hiking_date_vector_uk, "Hiking" ),
 stratifier(df, "EM_HY", "EM", Hiking_date_vector_us, "Hiking"),
 stratifier(df, "SA_HY", "SA", Hiking_date_vector_sa, "Hiking" ),
 stratifier(df, "SA_DG", "SA", Hiking_date_vector_sa, "Hiking" ),
 stratifier(df, "US_HY", "US", Hiking_date_vector_us, "Hiking" ), 
 stratifier(df, "US_DG", "US", Hiking_date_vector_us, "Hiking" )
 )

#  Cutting Perfromance

Cutting_performance <-  bind_rows(
 stratifier(df, "EU_HY", "EU", Cutting_date_vector_eu, "Cut" ),
 stratifier(df, "EU_DG", "EU_2", Cutting_date_vector_eu, "Cut" ),
 stratifier(df, "UK_HY", "UK", Cutting_date_vector_uk, "Cut" ),
 stratifier(df, "UK_HY_B", "UK", Cutting_date_vector_uk, "Cut" ),
 stratifier(df, "EM_HY", "EM", Cutting_date_vector_us, "Cut"),
 stratifier(df, "SA_HY", "SA", Cutting_date_vector_sa, "Cut" ),
 stratifier(df, "SA_DG", "SA", Cutting_date_vector_sa, "Cut" ),
 stratifier(df, "US_HY", "US", Cutting_date_vector_us, "Cut" ), 
 stratifier(df, "US_DG", "US", Cutting_date_vector_us, "Cut" )
 )

# Nuetral 

Nuetral_perfromance <-  bind_rows(
 stratifier(df, "EU_HY", "EU", Neutral_date_vector_eu, "Neutral" ),
 stratifier(df, "EU_DG", "EU_2", Neutral_date_vector_eu, "Neutral" ),
 stratifier(df, "UK_HY", "UK", Neutral_date_vector_uk, "Neutral" ),
 stratifier(df, "UK_HY_B", "UK", Neutral_date_vector_uk, "Neutral" ),
 stratifier(df, "JP_HY", "JP", Neutral_date_vector_jp, "Neutral" ),
 stratifier(df, "JP_DG", "JP", Neutral_date_vector_jp, "Neutral" ),
 stratifier(df, "EM_HY", "EM", Neutral_date_vector_us, "Neutral"),
 stratifier(df, "SA_HY", "SA", Neutral_date_vector_sa, "Neutral" ),
 stratifier(df, "SA_DG", "SA", Neutral_date_vector_sa, "Neutral" ),
 stratifier(df, "US_HY", "US", Neutral_date_vector_us, "Neutral" ), 
 stratifier(df, "US_DG", "US", Neutral_date_vector_us, "Neutral" )
 )

CB_df <- bind_rows(Nuetral_perfromance, 
 Cutting_performance, Hiking_performance) %>% arrange(Name)

CB_df

#  need to aggregate that into a single number 
```
- confident with this stratification
- huge idiosyncratic factors that have influenced the results thus performance of equity within each region. We will not get into that for now. 
- for HY returns, EM  H>C>N. EU N>C>H, SA H>C>N, UK H>C>N , US C>H>N
- for DG returns, US H>C>N, SA H>C>N,  EU N>C>H
- so HY indexes generally perform well in rising interest rate environments and have the lowest return in Neutral interest rate environments and DG dividend growth strategies follow a similar pattern. 
- Similar to the market cycle stratification, some regimes have less data points than other which may affect the returns. 

Within geographies then, EM - HY (H), EU - DG (C), JP - HY (N) , SA-DG (H) , UK HY - B  (H), US_DG (H), So mostly perform well in Hiking periods but their strategies are evenly split given our sample. 


# rolling consistency in returns

- How much bang for buck do these strategies give and how consistent are there at acheiving said return

To do this we will first 

- calculate the returns for both benchmark and index and get the tracking error of the each index to its benchmark.
- then simply on a rolling basis depict the movement of each pair. 
- we then graph that. 


```{r}
#  source 

source("code/InformationRatioRoll.R")

a <-  df %>% Information_Ratio_Roll(., "EU_HY", "EU", 20030808, 36)
b <-  df %>% Information_Ratio_Roll(., "EU_DG", "EU_2",20030808, 36)
 c <- df %>% Information_Ratio_Roll(., "UK_HY", "UK", 20030808, 36)
 d <- df %>% Information_Ratio_Roll(., "UK_HY_B", "UK", 20030808, 36)
 e <- df %>% Information_Ratio_Roll(., "JP_HY", "JP", 20030808, 36)
 f <- df %>% Information_Ratio_Roll(., "JP_DG", "JP", 20030808, 36)
 g <- df %>% Information_Ratio_Roll(., "EM_HY", "EM", 20030808, 36)
 h <- df %>% Information_Ratio_Roll(., "SA_HY", "SA", 20030808, 36)
 i <- df %>% Information_Ratio_Roll(., "SA_DG", "SA", 20030808, 36)
 j <- df %>% Information_Ratio_Roll(., "US_HY", "US", 20030808, 36)
 k <- df %>% Information_Ratio_Roll(., "US_DG", "US_2", 20030808, 36)

consistency_df <- list(a, b, c, d, e,f,g,h,i,j,k) %>%
  reduce(inner_join, by='date') %>% 
  gather(IR , ret, -date) 
 
plot <- consistency_df %>%   ggplot() + 
geom_line(aes(date, ret), color = "steelblue", size = 1.1, alpha = 0.8) +
geom_hline(yintercept = 0, color = "red", size = 0.3, alpha = 0.5)+
fmxdat::theme_fmx() + 
facet_wrap(~IR) + 
labs(x = "", y = "Information Ratio", title = "Performance Consistency", subtitle = "Deeply Inconcsistent", caption = "Source:Bloomberg and\n Authors Calculations")

plot

```
- the analysis here should take a different form. lets do this by sections. 
- HY indexes at the start had positive IR. Expect for SA and UK 
- Barring SA from pre 2010 there have moved into negative. 
- DG indexes start negative expect for the US. Apart from the slight postive in recent times from the US all are negative. 
- For regions with DG and HY portfolios, the consistency of returns tends to mirror each other. Given their characterization, their drivers should broadly be similar. 
- Comparing amongst regions, visually US and SA HY as off late have mirroring effects, and this term is used very loosely.There has been a general co movement  in IR for the different JP EM. 
- SA DG, SA HY and JP DG have had similar movements pre 2010 and more recently an upward trend. 

Possible analysis could be to regress the information ratios on a set of economic variables. Maybe do a rolling R2 of variables that may have an effect on the consistency of returns. 



# Trailing Performance and Drawdowns

A trailing return measures returns between two dates. They are also known as point-to-point returns since you are looking at performance between a starting date and an end date. It shows a snapshot of the mutual fund at a specific point in time. This metric can be used to measure returns year-to-date, one year, three years and so on. Trailing returns can also be calculated from the current date from the fund's inception date. This will be important to evaluate the how different inception dates affects fund performance.

Downwards give a more detailed picture of the risk attributes of the constituents of a data series. Their importance for our study is to uncover latent relationship between performance and drawdown.

```{r}

# lets get cumulative returns for our dividend strategies and Max drawdowns


cum_df <- excess_return_df %>%
  rename_all(~paste0("Excess from ", .)) %>% rename( "date" = "Excess from date") %>% 
  gather(Funds, ret, -date) %>% mutate(Year = format(date, "%Y")) %>% group_by(Year, Funds) %>% summarize(DD = (max(ret) - min(ret))/max(ret)* 100, Range = range(ret)) %>% arrange(desc(Range)) 

 order <- cum_df %>% pull(Funds) %>% unique()

cum_df$Year <- as.Date(paste0(cum_df$Year, "-01-01"))

source("code/order.R")

cum_df %>% 
  plot_order(., Column = "Funds", Order = order) %>% 
  ggplot() +
  geom_line(aes(Year, DD), color = "steelblue", size = 1.1, alpha = 0.8) + 
fmxdat::theme_fmx() + 
facet_wrap(~Funds) + 
labs(x = "", y = " Max Drawdowns (%)", title = "Yearly Drawdowns", subtitle = "", caption = "Source:Bloomberg and\n Authors Calculations")

plot

?range

# lets pick those that have had a significant amount of drawdowns over time
```
Draw downs in this study are defined as the difference between low and high values of cumulative excess returns within a time period. From our dividend portfolios we notice that drawdowns are similar in regions and across strategies. Both portfolios in SA show significant drawdowns by values followed by  UK HY strategies and with the EU and US strategies having the least amount of drawdowns. However, considering the dispersion of the drawdowns, we note that the UK High Yield and Japan High Yield strategies are suspectible to large changes, with emerging markets and south africa show the least variation.    


# Final Thoughts

Dividend portfolios either HY or DGPS have overtime give some level of positive return, as measured by the cumulative return. 
However, HY indexes give above average excess return for the sample period. Overtime however, most portfolios have choppy excess cumulative returns. There is no super convincing signal that these portfolios give some consistent excess return. 

The moment we stratifying according to different periods of volatility we notice that during periods of high volatility, its less the type of signal and more of the region that plays a big part in explaining the performance. in that case emerging market assets perform better than in low volatility environments. Unusual given in this time there is a flight to safety and EM will be risky at this time. During periods of low vol, advanced market portfolios generally give higher returns that in high vol conditions. 

When we consider rolling returns, excess returns for most portfolios move in a similar direction, generally there are part of the same asset class, exposed to the same risk factors and should behave the same way.  with the exception the SA portfolios. we notice that over three years, it has great variance in excess returns. This too can be said about the UK high yield portfolio. 

So what I can pick out is that dividend portfolios in EM behave different from advanced economies. 

To do 
- Will stratifying further, look at mid vol, inflation and interest rates? 

Working on the data section, where i describe the portfolios and their return signalling, 

Looked at cumulative excess return. no clear signal but for two HY portfolios. 
tratification, all portfolios perform as expected 

#     




