---
output:
  md_document:
    variant: markdown_github
---

# Objective

The goal is to assess the performance of dividend yield as an investment strategy. I plan to use optimized portfolios of the highest paying dividend stock and/or highest growth in dividends for a group of assets.

- First calculate the excess returns for indices and their benchmarks
- Explain relationships within the return series for each region with and without stratifying the sample. 
- Then maybe look to build own dividend portfolios to see how that would have performed.

# Instruments 

The global dividend portfolios considered in the table below are sourced from various literature from a practitioner perspective. They represent stylized portfolio constructed from respective market indexes. Using a similar approach I will consider broad market indices that are used to construct the dividend portfolios listed below.

```{r Instruments, echo=FALSE, message=FALSE, warning=FALSE}
library(knitr)
Table_data <- readxl::read_xlsx("data/Systematic Indices and Benchmarks.xlsx")
knitr::kable(Table_data) 
```

##  Excess Return

Excess returns here are calculated as the difference between cumulative index return and benchmark return. 

```{r echo=FALSE, message=FALSE, warning=FALSE}
# loadings 
pacman::p_load("xts", "tidyverse", "tbl2xts", "PerformanceAnalytics", 
               "lubridate", "glue")
library(tbl2xts)
library(tidyverse)
library(xts)
source("code/EXCESSRETURN.R")

df <- readxl::read_xlsx("data/MAD .xlsx")


# get all permutatation 
A <- df %>% MY_excess_return(.,"FUDP", "TUKXG") 
B <- df %>% MY_excess_return(., "M2EFDY", "GDUEEGF") 
C <- df %>% MY_excess_return(., "M2EUGDY", "GDDUE15X") 
D <- df %>% MY_excess_return(., "M2GBDY", "GDDUUK") 
E <- df %>% MY_excess_return(., "M2JPDY", "TJDIVD") 
F1 <- df %>% MY_excess_return(., "M2USADVD", "GDDUUS") 
G <- df %>% MY_excess_return(., "M2WDHDVD", "GDDUWI") 
H <- df %>% MY_excess_return(., "SPDAEET", "SPTR350E") 
I <- df %>% MY_excess_return(., "SPDAUDT", "SPXT") 
J <- df %>% MY_excess_return(., "SPJXDAJT", "TPXDDVD") 
K <- df %>% MY_excess_return(., "SPSADAZT", "JALSH") 
L <- df %>% MY_excess_return(., "TJDIVD", "JALSH")

joined_df <- bind_cols(A, B, C, D, E, F1, G, H, I, J, K, L) 

compare <- joined_df %>% select(date...1, FUDP, M2EFDY, M2EUGDY, M2GBDY, M2JPDY, M2USADVD, M2WDHDVD, SPDAEET, SPDAUDT, SPJXDAJT, SPSADAZT, TJDIVD) %>% gather(Index , Return , -date...1)

plot <- compare %>% ggplot(aes(x = date...1, y = Return, color = Index)) +
  geom_line() +
  labs(x = "Date", y = "Return", color = "Index") +
  theme_minimal() +
  facet_wrap(~ Index, scales = "free_y", ncol = 4)

plot
```




