---
output:
  md_document:
    variant: markdown_github
---

# Objective

The goal is to assess the performance of dividend yield as an investment strategy. I plan to optimize portfolios of the highest paying dividend stock and/or highest growth in dividends for a group of assets.

- First calculate the excess returns for indices and their benchmarks
- Explain relationships within the return series for each region with and without stratifying the sample. 
- Then maybe look to build own dividend portfolios to see how that would have performed.

# Instruments 

To investigate the performance of dividend paying strategies, either dividend yield or dividend growth I will consider globally traded indices and their benchmarks. For concreteness, I will look at those prescribed in literature. From this I will find the excess return. 

```{r Instruments, echo=FALSE, message=FALSE, warning=FALSE}
Table_data <- readxl::read_xlsx("data/Instruments from MAD.xlsx")
library(knitr)
kable(Table_data)
```

##  Excess Return

I calculate excess returns as the monthly difference return for index and benchmark, then calculate cumulative returns for the result. 

The indices across regions have different inception dates therefore not purely comparable across regions. 

From the figure below, results of dividend strategies (High Yield or Dividend Growth) at different inception dates have been consistently returned  a positive excess over the market index, even though sometimes volatile.  This shows full sample performance. 

- consider the mix between high dividend yield versus dividend growth portfolios, so color coordinate the different strategies?

```{r echo=TRUE, message=FALSE, warning=FALSE}
# loadings 
pacman::p_load("xts", "tidyverse", "tbl2xts", "PerformanceAnalytics", 
               "lubridate", "glue")
library(tbl2xts)
library(tidyverse)
library(xts)
source("code/EXCESSRETURN.R")
source("code/EXCESSRETURN2.R")
source("code/monthlyreturns.R")
library(quantmod)
source("code/uncompoundedexcess.R")
source("code/simpleexcessreturn.R")

df <- readxl::read_xlsx("data/MAD .xlsx") 

# get all permutatation 
A <- df %>% MY_excess_return(.,"FUDP", "TUKXG") 
B <- df %>% MY_excess_return(., "M2EFDY", "GDUEEGF") 
C <- df %>% MY_excess_return(., "M2EUGDY", "GDDUE15X") 
D <- df %>% MY_excess_return(., "M2GBDY", "GDDUUK") 
E <- df %>% MY_excess_return(., "M2JPDY", "TJDIVD") 
F1 <- df %>% MY_excess_return(., "M2USADVD", "GDDUUS") 
G <- df %>% MY_excess_return(., "M2WDHDVD", "GDDUWI") 
H <- df %>% MY_excess_return(., "SPDAEET", "SPTR350E") 
I <- df %>% MY_excess_return(., "SPDAUDT", "SPXT") 
J <- df %>% MY_excess_return(., "SPJXDAJT", "TPXDDVD") 
K <- df %>% MY_excess_return(., "SPSADAZT", "JALSH") 
L <- df %>% MY_excess_return(., "TJDIVD", "JALSH")

#  cumulative excess returns in a single data frame
compare <- list(A, B, C, D, E, F1, G,H,J, K, L) %>%
  reduce(inner_join, by='date') %>% gather(ticker, excess, -date)

plot <- compare %>% ggplot(aes(x = date, y = excess)) +
  geom_line() +
  labs(x = "Date", y = "Return") +
  theme_minimal() +
  facet_wrap(~ ticker, scales = "free_y", ncol = 4)+
   labs(
    title = "Cumulative Excess Returns",
    subtitle = "Start dates differ amongst portfolios",
    x = "",
    y = "Cum Returns",
    caption = "Source: Bloomberg"
  )

plot

# Now for standard deviation 
```

## Stratification 

Applying a top down approach means that it would be prudent to consider returns of the dividend portfolios under different time periods 

I will use volatility and interest rate cycles. 

- For volatility I will use the historical series for the CBOE VIX index. I will get the roll standard deviation and separate values according to their percentile to get periods that expirienced the most volatility during the period. then bucket the two periods in either low or high vol So periods of high volatility and low volatility. 

- then annulized measure to get out excess returns on a three, five and ten year basis. 

- For interest rate cycles use periods of interest cutting and hiking. 

_ rolling returns, cant you rank them on

```{r echo=TRUE, message=FALSE, warning=FALSE}
# get vol data from yahoo 

vix <- getSymbols("VIX")
VIX <- VIX %>% tbl2xts::xts_tbl(.)
VIX <- VIX %>% select(date, VIX.Close)

# get rolling sd for the volatility index 

Roll.sd <- VIX%>% rename(Close = VIX.Close) %>% 
  mutate(Ret = log(Close)- lag (log(Close))) %>% 
  filter(date > first(date)) %>% 
  mutate(RollSD = RcppRoll::roll_sd(1 + Ret, 12, fill = NA, align = "right") * 
    sqrt(12))

Roll.sd <- Roll.sd %>% filter(!is.na(RollSD))

# get the top quartile and bottom quartile

strat_df <- 
Roll.sd %>% mutate(topQ = quantile(RollSD, probs = 0.8), 
              botQ = quantile(RollSD, probs = 0.2),
              Strat = ifelse(RollSD >= topQ, "HiVol", 
                          ifelse(RollSD <= botQ, "LowVol", "Normal_Vol")))

hivol_per_vector <- strat_df %>% filter(Strat %in% "HiVol") %>% pull(date)
lovol_per_vector <- strat_df %>% filter(Strat %in% "LowVol") %>% pull(date)


# get entire returns and apply the vector above 
# voldata <-df %>% monthlyret(.) 

# get all permutatation 
A <- df %>% simple_excess_return(.,"FUDP", "TUKXG") 
B <- df %>% simple_excess_return(., "M2EFDY", "GDUEEGF") 
C <- df %>% simple_excess_return(., "M2EUGDY", "GDDUE15X") 
D <- df %>% simple_excess_return(., "M2GBDY", "GDDUUK") 
E <- df %>% simple_excess_return(., "M2JPDY", "TJDIVD") 
F1 <- df %>% simple_excess_return(., "M2USADVD", "GDDUUS") 
G <- df %>% simple_excess_return(., "M2WDHDVD", "GDDUWI") 
H <- df %>% simple_excess_return(., "SPDAEET", "SPTR350E") 
I <- df %>% simple_excess_return(., "SPDAUDT", "SPXT") 
J <- df %>% simple_excess_return(., "SPJXDAJT", "TPXDDVD") 
K <- df %>% simple_excess_return(., "SPSADAZT", "JALSH") 
L <- df %>% simple_excess_return(., "TJDIVD", "JALSH")

#  cexcess returns in a single data frame
excessreturns <- list(A, B, C, D, E, F1, G,H,J, K, L) %>%
  reduce(inner_join, by='date') %>% gather(ticker, excess, -date)

# hivol <- voldata %>%
#   filter(Date %in% hivol_per_vector) %>% 
#   filter(Date >= fmxdat::safe_month_min(last(Date), N = 36)) %>%
#   group_by(Tickers) %>% 
#   summarise(Hivol_return = prod(1+ret, na.rm=T) ^ (12/(36)) -1 ) 
# 
# lovol <-  voldata %>%
#   filter(Date %in% lovol_per_vector) %>% 
#   filter(Date >= fmxdat::safe_month_min(last(Date), N = 36)) %>%
#   group_by(Tickers) %>% 
#   summarise(Lovol_return = prod(1+ret, na.rm=T) ^ (12/(36)) -1 ) 

hivol <- excessreturns %>%
  filter(date %in% hivol_per_vector) %>% 
  filter(date >= fmxdat::safe_month_min(last(date), N = 36)) %>%
  group_by(ticker) %>% 
  summarise(Hivol_return = prod(1+excess, na.rm=T) ^ (12/(36)) -1 ) 

lovol <-  excessreturns%>%
  filter(date %in% lovol_per_vector) %>% 
  filter(date >= fmxdat::safe_month_min(last(date), N = 36)) %>%
  group_by(ticker) %>% 
  summarise(lovol_return = prod(1+excess, na.rm=T) ^ (12/(36)) -1 ) 

volreturns <- left_join(hivol, lovol, by = "ticker") %>% 
  mutate(trend = case_when(
    Hivol_return > lovol_return ~ "higher",
    TRUE ~ "lower"
  ))

kable( volreturns)


# rolling returns 

plotdf <- excessreturns %>% 
  group_by(ticker) %>% 
  mutate(RollRets = RcppRoll::roll_prod(1 + excess, 36, fill = NA, 
    align = "right")^(12/36) - 1) %>% 
  group_by(date) %>% filter(any(!is.na(RollRets))) %>% 
  ungroup()

g <- ggplot(plotdf, aes(date, RollRets, color = ticker)) +
  geom_line(alpha = 0.5, size = 1) +
  labs(
    title = "Rolling 3 Year Annualized Returns",
    subtitle = "",
    x = "",
    y = "Rolling 3 year Returns (Ann.)",
    caption = "Source: Bloomberg"
  )
g




```
# Observations

- we have dividend portfolios of HY and DGPS in US, UK, JAPAN, EM and SA. 

In cumulative returns
- FUDP (HY) had the most impressive

These next two show marginal improvements over market indices
- M2EUGDY 
- M2GBDY 

Overall a positive excess return does show some gain to harvesting such portfolios. 

Stratification analysis 

If we just consider the level of volatility in global financial markets. we can see a clear trend. 

- most poortfolios give lower returns when in high vol versus low vol 
- except for SPSADAZT, TJDIVD, SPDAEET and M2EFDY.

Rolling returns 

Overall, massive divergence followed by a convergence in rolling excess returns. There is some divergence towards the end of the sample period. 

- FUDP, SPSADAZT, TJDIVD visually have massive varinace in their rolling excess returns. 

- Others dont have worrying movements in rolling returns




